---
title: "MCDielLight"
author:
- Douglas A. Campbell
- Sylwia Wilczewska-Wilinska
- Mireille Savoie
date: "`r format(Sys.Date())`"
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---
# Introduction

# This exploratory Rmd loads previously imported, tidied data from the PSI MC and generates estimates of hourly and diel cumulative photon dose to cultures. This can be run for any PSI MC data file.
  
# IF AVAILABLE it imports Chl, Cell, light response equations and calibrations for JVPSII, IF AVAILABLE, to estimate time resolved JVPSII per cell and per chl..
# These calibrations are not fully available for Prochlorococcus.

# It then explores plots of hourly time resolved growth rates, vs. hourly cumulative photon dose, and hourly JVPSII if available

# It is too long.

# We have only limited JVPSII data with little to no intra-diel resolution of any changes in the JVPSII vs. light response curves;  if morning JVPSII is, as likely, different from afternoon JVPSII, we would not capture this, as yet.
# Sylwia has some intra-diel time resolved OLIS & JVPSII data every 2 hours; 2 light levels; 1 photoperiod; 2 strains?  measurements taken when steps biggest...

# Where necessary reset ToD to CultureToD with 0 at middle of scotoperiod and 12 at middle of photoperiod;  Sylwia different than Mireille sometimes;  Sylwia 13:00 is 'noon'

# Doug fix ToD where needed
# Doug check issue where JVPSII vs. ToD does not match PAR vs ToD; surprising
  Is it worth messing with JVPSII for data sets in which we do not have intraday JVPSII resolution.   JVPSII is a slightly saturating transform of PAR; so plots are similar to PAR
  
# Set Options

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r libraries}
library(zoo)
library(tidyverse)
library(purrr)

# library(dplyr)
# library(e1071)
# library(gcookbook)  # Load gcookbook for the uspopage data set
#library(viridis)  # Load viridis for the viridis palette
library("RColorBrewer")
```

```{r colour setting}
# Bin4_nm <- c(440, 510, 590, 660)
# Bin4Colours <- c(w_length2rgb(440), w_length2rgb(510), w_length2rgb(590), w_length2rgb(660))
# names(Bin4Colours) <- Bin4_nm
```


```{r set project variables}
Project <- "PicoDiel"
DataIn <- file.path("..", "Data", "CleanedData", "CleanedMCData")
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedMCDielLightData")


FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

## Chl and Cell calibrations

```{r chl and cell calibrations}
# ChlCellCalib <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData", "PicoDiel_Imported_CrossCalibrationData.Rds"))

# test <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData", "PicoDiel_Tab_MDPicoMCODCorrelation.Rds"))
```


## Read Data
Check with Sylwia & Mireille about what filter(s) have been applied in 'Process' Consider using 'Process' before this step
```{r data files}
MCFiles <- list.files(path = file.path(DataIn), full.names = TRUE)
MCFiles
```

```{r read data and select relevant columns}

MCData <- readRDS(file = MCFiles[2])

glimpse(MCData)

MCData <- MCData %>% 
  select(c(Strain,WL, SampleID, Run, Par_ue, Pur_ue, ObsDate, E_days, PurData, PurParRatio, PARPhotonDose_day, PURPhotonDose_day, Filename, Tube, ExpDate, MC, PrimaryOperator, Photoperiod, ExpEndHour, O2_uM, tubedata, OD720_logistic_predict, deltaOD_logistic_predict, OD720_Lmu_corr, deltaOD_Lmu_corr))

```

```{r par_time_plot}
MCData |>
  filter(Run == 114) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
  filter(Run == 114) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 48,
         tubedata_time <= 72) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
 filter(Run == 114) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 48,
         tubedata_time <= 72) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
 filter(Run == 114) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 48,
         tubedata_time <= 72) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par)) +
  geom_point(aes(x = tubedata_time, y = 1000 * tubedata_deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
  filter(Run == 114) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  # filter(tubedata_time >= 48,
  #        tubedata_time <= 72) |>
  filter(Tube == 3) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par)) +
  geom_point(aes(x = tubedata_time, y = 10000 * tubedata_deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()
```

#https://stackoverflow.com/questions/76603287/calculate-linear-regression-slope-with-moving-window


Seeking rolling window with width of 12 rows; 5 min per row, 60 min window;
-why is rollapply NA for first 5 rows; why not 12 rows?;
-why are mu not as expected from manual?
  Solved with align = "right" and align = "left"

```{r growth rates}

#slope <- function(x) coef(lm(x[, 2] ~ x[, 1]))[[2]] #same result, much slower
slope <- function(x) cov(x[, 1], x[, 2]) / var(x[, 1])

#FitWindow_h <- 2
#maybe issues still with changes in light level that do not align with growth measurement points

#maybe should estimate growth rates, then use 'summarize' to do sum of actinic photon dose for each hour?

ODinterval <- 5

# DielLightGrowthPro <- MCData |>
#   filter(Run == 114) |>
#   group_by(Filename, Tube) |>
#    mutate(Actinic_umolphotonsm2h = zoo::rollsum(tubedata_Actinic_par * 60 * ODinterval , k = 60/ODinterval, fill = NA, align = "right")) |> #PAR per h
#   mutate(mu_OD720window = zoo::rollapply(cbind(time, log(OD720)), width = 60/ODinterval, FUN = slope, by.column=FALSE, fill=NA, align = "right")) |> #slope
#   mutate(mu_Averh = zoo::rollmean(mu_OD720window, k = 60/ODinterval, fill = NA, align = "left")) |> #average of first 12 row  ungroup() 
# filter(time - round(time) == 0) #crude collapse to 1 measurement per hour

DielLightGrowthPro <- MCData |>
  # filter(Run == 114) |>
  unnest(cols = c(tubedata)) |>
   group_by(Filename, Tube) |>
   mutate(Actinic_umolphotonsm2h = zoo::rollsum(Actinic_par * 60 * ODinterval , k = 60/ODinterval, fill = NA, align = "right")) |> #PAR per h
  mutate(mu_OD720window = zoo::rollapply(cbind(time, log(OD720)), width = 60/ODinterval, FUN = slope, by.column=FALSE, fill=NA, align = "right")) |> #slope
  mutate(mu_Averh = zoo::rollmean(mu_OD720window, k = 60/ODinterval, fill = NA, align = "left")) |> #average of first 12 row  ungroup() 
filter(time - round(time) == 0) |> #crude collapse to 1 measurement per hour
nest(tubedata = c(time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720,
                  ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD,Actinic_umolphotonsm2h, mu_OD720window, mu_Averh))


```



```{r preliminary plot}
DielLightGrowthPro |>
  filter(Run == 114) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
  #        time <= 72) |>
  #filter(time < 100) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h)) +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "green") +
  facet_grid(cols = vars(Tube), rows = vars(Filename)) +
  theme_bw()

```


```{r hourly plots exploration}
#temporary
#use case_when to remove 'dark' periods?
#bad to filter and only then estimate growth rates; better to do across 1 h window


DielLightGrowthPro |> 
  filter(Run == 114) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
   filter(tubedata_time <= 96) |>
  ggplot() +
  geom_point(aes(x = tubedata_Actinic_umolphotonsm2h, y = tubedata_mu_Averh, colour = tubedata_ToD)) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

DielLightGrowthPro |>
    filter(Run == 114) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
   filter(tubedata_time <= 96) |>
  ggplot() +
  geom_point(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h)) +
  geom_line(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h)) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

DielLightGrowthPro |>
    filter(Run == 114) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
   filter(tubedata_time <= 96) |>
  filter(Tube == 3) |>
  ggplot() +
  geom_point(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h)) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

```

```{r save hourly growth}
 # saveRDS(object = DielLightGrowthPro, file = file.path(DataOut, "DielLightGrowthPro.Rds"), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```

