---
title: "DielLightGrowthJVPSII"
author:
- Douglas A. Campbell
- Sylwia Wilczewska-Wilinska
- Mireille Savoie
date: "`r format(Sys.Date())`"
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---
# Introduction - this is an incomplete skeleton.

# This exploratory Rmd loads previously generated estimates of hourly and diel cumulative photon dose to cultures run in MultiCultivators.
  
# IF AVAILABLE it imports Chl, Cell, light response equations and calibrations for JVPSII, IF AVAILABLE, to estimate time resolved JVPSII per cell and per chl..
# These calibrations are not fully available for Prochlorococcus.

# It then explores plots of hourly time resolved growth rates, vs. hourly cumulative photon dose, and hourly JVPSII if available

# We have only limited JVPSII data with little to no intra-diel resolution of any changes in the JVPSII vs. light response curves;  if morning JVPSII is, as likely, different from afternoon JVPSII, we would not capture this, as yet.
# Sylwia has some intra-diel time resolved OLIS & JVPSII data every 2 hours; 2 light levels; 1 photoperiod; 2 strains?  measurements taken when steps biggest...


# Doug check issue where JVPSII vs. ToD does not match PAR vs ToD; surprising
  Is it worth messing with JVPSII for data sets in which we do not have intraday JVPSII resolution.   JVPSII is a slightly saturating transform of PAR; so plots are similar to PAR
  
# Set Options

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r libraries}
library(tidyverse)
library(zoo)

library(e1071)
library(gcookbook)  # Load gcookbook for the uspopage data set
#library(viridis)  # Load viridis for the viridis palette
library("RColorBrewer")
```

```{r colour setting}
# Bin4_nm <- c(440, 510, 590, 660)
# Bin4Colours <- c(w_length2rgb(440), w_length2rgb(510), w_length2rgb(590), w_length2rgb(660))
# names(Bin4Colours) <- Bin4_nm
```

```{r set project variables}
Project <- "PicoDiel"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedMCDielLightData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

## Chl and Cell calibrations

```{r chl and cell calibrations}
# ChlCellCalib <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData", "PicoDiel_Imported_CrossCalibrationData.Rds"))

test <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData", "PicoDiel_Tab_MDPicoMCODCorrelation.Rds"))
```



## JVPSII light response and calibrations
Think about how to calibrate JVPSII; what does it mean?  Use e cell-1 s-1?
Need to import calibrations to convert OD720 to cell L-1 and OD680 to chl L-1
```{r jvpsii}

#JVPSII_eLs_ModelTerms <- readRDS(file = file.path("..", "Data","CleanedData", "JVPSII_eLs_ModelTerms.Rds"))

#need to filter and summarize data to get single calibration for each SampleID...

Processed_Solisense_LRC <- readRDS(file = file.path("..", "Data","CleanedData", "Processed_Solisense_LRC.Rds")) |>
select(-c("data")) |>
  filter(Ex_WL == 445) |> #temporary hack; later do spectrally weighted estimates
  unnest(GRCplatt_Param) |>
  select(-c("std.error", "statistic", "p.value")) |>
  pivot_wider(names_from = c( term, Ex_WL,), values_from = c(estimate)) |>
  filter(E_days < 8,
         E_days > 2) |>
  group_by(SampleID) |>
  summarize(across(`a_445`:`Pmax_445`, mean))  # hack temporary fix to collapse duplicated LRC parameters for the same SampleID
```


## Read Hourly Data

# JVPSII exploration
# Need to import JVPSII e cell-1 s-1 or e- chl-1 s-1 instead of e L-1 s-1 for generalization
```{r jvpsii eLs 445}
#lrcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

#worried about unit conversions here!
MCDataHour2 <- MCDataHour |>
  filter(SampleID %in% intersect(unique(Processed_Solisense_LRC$SampleID), unique(MCDataHour$SampleID))) |> #hack to match JVPSII LRC estimators to available files
  left_join(Processed_Solisense_LRC, by = c("SampleID")) |> mutate(JVPSII_umoleLh = 3600 * (Pmax_445 *  (1 - exp((-a_445*Actinic_umolphotonsm2h/3600)/(Pmax_445)) * exp(-b_445*Actinic_umolphotonsm2h/3600/(Pmax_445))                                                                                             )                                                                                           )
)

#FIX THIS PROPERLY: it is a quick hack

# lrcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}
# 
# 
# SolFitsMetaLRC <- SolFitsMeta %>%
#   nest(data = -c("SampleID", "Run", "Strain" ,"ExpDate","Par_ue", "Photoperiod", "O2", "WL", "MC", "Tube","Ex_WL","LightShape", "ExpEndDate", "PARPhotonDose_day", "ObsDate", "E_days")) %>% #head(50) %>% 
#   mutate(lrcplatt_Model = map(data, possibly(~nlsLM(JVPSII_umol_eLs ~ lrcplatt(I = ActPARCorr, a, b, Pmax),
```


```{r explore jvpsii}
MCDataHour2 |>
  filter(Run == 39) |>
  filter(time >= 24) |>
  filter(time <= 96) |>
  #filter(Tube == 4) |>
  ggplot() +
  # geom_point(aes(x = Actinic_umolphotonsm2h, y = mu_Averh, colour = ToD)) +
  # scale_color_gradient(low = "black", high = "yellow") +
  geom_point(aes(x = Actinic_umolphotonsm2h, y = JVPSII_umoleLh, colour = ToD)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour2 |>
  filter(Run == 39) |>
  filter(time >= 24) |>
  filter(time <= 96) |>
  #filter(Tube == 4) |>
  ggplot() +
  # geom_point(aes(x = Actinic_umolphotonsm2h, y = mu_Averh, colour = ToD)) +
  # scale_color_gradient(low = "black", high = "yellow") +
  geom_point(aes(x = ToD, y = JVPSII_umoleLh, colour = Actinic_umolphotonsm2h)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour2 |>
  filter(Run == 39) |>
  filter(time >= 24) |>
  filter(time <= 96) |>
  #filter(Tube == 4) |>
  ggplot() +
  # geom_point(aes(x = Actinic_umolphotonsm2h, y = mu_Averh, colour = ToD)) +
  # scale_color_gradient(low = "black", high = "yellow") +
  geom_point(aes(x = JVPSII_umoleLh, y = mu_Averh, colour = Actinic_umolphotonsm2h)) +
  #facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour2 |>
  filter(Run == 39) |>
  filter(time >= 24) |>
  filter(time <= 96) |>
  #filter(Tube == 4) |>
  ggplot() +
  # geom_point(aes(x = Actinic_umolphotonsm2h, y = mu_Averh, colour = ToD)) +
  # scale_color_gradient(low = "black", high = "yellow") +
  geom_point(aes(x = Actinic_umolphotonsm2h, y = mu_Averh, colour =  JVPSII_umoleLh)) +
  #facet_grid(cols = vars(Tube)) +
  theme_bw()


```
Some JVPSII vs. ToD (tube 4) look surprising?   What is happening?

