---
title: "DielLightGrowthPeaks"
author:
- Douglas A. Campbell
- Sylwia Wilczewska-Wilinska
- Mireille Savoie
date: "`r format(Sys.Date())`"
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---
# Introduction - skeleton

This exploratory Rmd loads estimates of hourly and diel cumulative photon dose to cultures generated from PSI MC data file.

It plots timing of peaks of growth rates vs. peaks of PAR and ToD to detect shifts in timing with growth conditions & strain.

  
# Set Options

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r libraries}
library(tidyverse)
library(zoo)

library(e1071)
library(gcookbook)  # Load gcookbook for the uspopage data set
#library(viridis)  # Load viridis for the viridis palette
library("RColorBrewer")
```

```{r colour setting}
# Bin4_nm <- c(440, 510, 590, 660)
# Bin4Colours <- c(w_length2rgb(440), w_length2rgb(510), w_length2rgb(590), w_length2rgb(660))
# names(Bin4Colours) <- Bin4_nm
```

```{r set project variables}
Project <- "PicoDiel"
DataOut <- file.path("..", "Data", "ProcessedData", "DielLightPeaks")

FigPath <- file.path("..", "Output", "Figures")
# FigRdsPath <- file.path("..", "Output", "FiguresRds")
# TableRdsPath <- file.path("..", "Output", "TablesRDS")
```



## Read Data


```{r read data}
DielData <- readRDS(file = file.path("..", "Data", "ProcessedData", "ProcessedMCDielLightData","DielLightGrowth.Rds"))
```

# Exploratory Plots from representative data file
```{r par_time_plot}
DielData |>
  filter(Run == 39) |>
  ggplot() +
  geom_point(aes(x = ToD, y = Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()


```




```{r preliminary plot}
DielData |>
  filter(Run == 39) %>% 
  filter(time >= 24) |>
  #        time <= 72) |>
  #filter(time < 100) |>
  ggplot() +
  geom_point(aes(x = ToD, y = mu_Averh, colour = Actinic_umolphotonsm2h)) +
  #geom_point(aes(x = time, y = OD720), colour = "green") +
  facet_grid(cols = vars(Tube), rows = vars(Filename)) +
  theme_bw()

```
#Estimate minium & maximum growth rate for each day
Also think about 'compensation point' where growth passes 0

```{r minmax_growth}
#use nest or group_by?

DielData |>
  filter(Run == 39) |> 
  filter(time >= 24) |>
  #filter(time < 100) |>
  group_by(Filename, Tube, Day) |>
  mutate(MinMu = min(mu_Averh, na.rm = TRUE),
         MaxMu = max(mu_Averh, na.rm = TRUE),
         MinToD = ToD[which(mu_Averh == min(mu_Averh, na.rm = TRUE))],
         MaxToD = ToD[which(mu_Averh == max(mu_Averh, na.rm = TRUE))]
  ) |>
   ggplot() +
  geom_point(aes(x = ToD, y  = Actinic_umolphotonsm2h), colour = "Yellow") +
  geom_point(aes(x = MaxToD, y  = MaxMu)) +
  #geom_point(aes(x = time, y = OD720), colour = "green") +
  facet_grid(cols = vars(Tube), rows = vars(Filename)) +
  theme_bw()
  
```




```{r save hourly growth peaks}
# add code with 'paste' to generate custom name later

# saveRDS(object = DielLightGrowth, file = file.path(DataOut, "DielLightGrowth.Rds"), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```


