---
title: "MCDielLight"
author:
- Douglas A. Campbell
- Sylwia Wilczewska-Wilinska
- Mireille Savoie
date: "`r format(Sys.Date())`"
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---
# Introduction

# This exploratory Rmd loads previously imported, tidied data from the PSI MC and generates estimates of hourly and diel cumulative photon dose to cultures. This can be run for any PSI MC data file.

# It then explores plots of hourly time resolved growth rates, vs. hourly cumulative photon dose, and hourly JVPSII if available

# Where necessary reset ToD to CultureToD with 0 at middle of scotoperiod and 12 at middle of photoperiod;  Sylwia different than Mireille sometimes;  Sylwia 13:00 is 'noon'


# Set Options

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r libraries}
library(zoo)
library(tidyverse)

# library(dplyr)
# library(e1071)
# library(gcookbook)  # Load gcookbook for the uspopage data set
#library(viridis)  # Load viridis for the viridis palette
library("RColorBrewer")
```

```{r colour setting}
# Bin4_nm <- c(440, 510, 590, 660)
# Bin4Colours <- c(w_length2rgb(440), w_length2rgb(510), w_length2rgb(590), w_length2rgb(660))
# names(Bin4Colours) <- Bin4_nm
```


```{r set project variables}
Project <- "PicoDiel"
DataIn <- file.path("..", "Data", "CleanedData", "CleanedMCData")
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedMCDielLightData")


FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

## Chl and Cell calibrations

```{r chl and cell calibrations}
# ChlCellCalib <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData", "PicoDiel_Imported_CrossCalibrationData.Rds"))

# test <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData", "PicoDiel_Tab_MDPicoMCODCorrelation.Rds"))
```


## Read Data
Check with Sylwia & Mireille about what filter(s) have been applied in 'Process' Consider using 'Process' before this step
```{r data files}
MCFiles <- list.files(path = file.path(DataIn), full.names = TRUE)
MCFiles
```

```{r read data and select relevant columns}

MCData <- readRDS(file = MCFiles[2])

glimpse(MCData)

MCData <- MCData %>% 
  select(c(Strain,WL, SampleID, Run, Par_ue, Pur_ue, ObsDate, E_days, PurData, PurParRatio, PARPhotonDose_day, PURPhotonDose_day, Filename, Tube, ExpDate, MC, PrimaryOperator, Photoperiod, ExpEndHour, O2_uM, tubedata, GrowthAmpOD720_14days, GrowthAmpdeltaOD_14days, OD720_logistic_predict, deltaOD_logistic_predict, OD720_Lmu_corr, deltaOD_Lmu_corr))

glimpse(MCData)

```

```{r par_time_plot}
MCData |>
  filter(Run == 87) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
  filter(Run == 87) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 48,
         tubedata_time <= 72) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
 filter(Run == 87) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 48,
         tubedata_time <= 72) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
 filter(Run == 87) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 48,
         tubedata_time <= 72) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par)) +
  geom_point(aes(x = tubedata_time, y = 1000 * tubedata_deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
  filter(Run == 87) |>
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) |>
  # filter(tubedata_time >= 48,
  #        tubedata_time <= 72) |>
  filter(Tube == 6) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par)) +
  geom_point(aes(x = tubedata_time, y = 10000 * tubedata_deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()
```


```{r remove all no growth tubes}

MCData <- MCData %>% 
  filter(deltaOD_Lmu_corr > 0)

```

#https://stackoverflow.com/questions/76603287/calculate-linear-regression-slope-with-moving-window


Seeking rolling window with width of 12 rows; 5 min per row, 60 min window;
-why is rollapply NA for first 5 rows; why not 12 rows?;
-why are mu not as expected from manual?
  Solved with align = "right" and align = "left"

```{r growth rates}

#slope <- function(x) coef(lm(x[, 2] ~ x[, 1]))[[2]] #same result, much slower
slope <- function(x) cov(x[, 1], x[, 2]) / var(x[, 1])

#FitWindow_h <- 2
#maybe issues still with changes in light level that do not align with growth measurement points

#maybe should estimate growth rates, then use 'summarize' to do sum of actinic photon dose for each hour?

ODinterval <- 5

  # mutate(OD720_logistic = map(tubedata, possibly(~nlsLM(OD720 ~ logistic_eqn(x = time, Lmax, Lmu, Lintercept),
  #                           data = .x,
  #                           start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),  
  #                                        Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time),
  #                                        Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),
  #                           control = list(maxiter = 500)), otherwise = NULL)),
  #        OD720_logistic_tidied =  map(OD720_logistic, possibly(tidy, otherwise = NULL)),
  #        OD720_logistic_param = map(OD720_logistic,possibly(glance, otherwise = NULL)),
  #        OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))
  #        )

# DielLightGrowthPro2 <- MCData |>
#    # filter(Run == 87) |>
#   # group_by(Filename, Tube) |>
#    mutate(Actinic_umolphotonsm2h = map(tubedata, zoo::rollsum(.$Actinic_par * 60 * ODinterval , k = 60/ODinterval, fill = NA, align = "right")))
#  
# DielLightGrowthPro2 <- MCData |>
#    # filter(Run == 87) |>
#   # group_by(Filename, Tube) |>
#    mutate(Actinic_umolphotonsm2h = map(tubedata, OD720)) 

# |> #PAR per h
#   mutate(mu_OD720window = zoo::rollapply(cbind(time, log(OD720)), width = 60/ODinterval, FUN = slope, by.column=FALSE, fill=NA, align = "right")) |> #slope
#   mutate(mu_Averh = zoo::rollmean(mu_OD720window, k = 60/ODinterval, fill = NA, align = "left")) |> #average of first 12 row  ungroup()
# filter(time - round(time) == 0) #crude collapse to 1 measurement per hour

DielLightGrowthPro <- MCData |>
  # filter(Run == 87) |>
  unnest(cols = c(tubedata)) |>
   group_by(Filename, Tube) |>
   mutate(Actinic_umolphotonsm2h = zoo::rollsum(Actinic_par * 60 * ODinterval , k = 60/ODinterval, fill = NA, align = "right")) |> #PAR per h
  mutate(mu_OD720window = zoo::rollapply(cbind(time, log(OD720)), width = 60/ODinterval, FUN = slope, by.column=FALSE, fill=NA, align = "right")) |> #slope
  mutate(mu_Averh = zoo::rollmean(mu_OD720window, k = 60/ODinterval, fill = NA, align = "left")) |> #average of first 12 row  ungroup() 
filter(time - round(time) == 0) |> #crude collapse to 1 measurement per hour
nest(tubedata = c(time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD,Actinic_umolphotonsm2h, mu_OD720window, mu_Averh)) %>% 
  ungroup()


```



```{r preliminary plot}
DielLightGrowthPro |>
  filter(Run == 87) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
  #        time <= 72) |>
  #filter(time < 100) |>
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h)) +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "green") +
  facet_grid(cols = vars(Tube), rows = vars(Filename)) +
  theme_bw()

```


```{r hourly plots exploration}
#temporary
#use case_when to remove 'dark' periods?
#bad to filter and only then estimate growth rates; better to do across 1 h window

#scale_color_gradient2 to have noon light, start and end of ToD dark


# DielLightGrowthPro |>
#     filter(Run == 87) %>% 
#    unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
#   filter(tubedata_time >= 24) |>
#    filter(tubedata_time <= 120) |>
#   ggplot() +
#   geom_point(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h), size = 0.1) +
#   geom_vline(xintercept = 12) +
#   scale_color_gradient(low = "black", high = "yellow") +
#   facet_grid(cols = vars(Tube)) +
#   theme_bw()


DielLightGrowthPro |>
  filter(Strain == "MED4",
         WL != 530,
         O2_uM == 25,
         Par_ue %in% c(30,90,180)) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
   filter(tubedata_time <= 120) |>
  ggplot() +
  geom_point(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h), size = 0.1) +
  geom_vline(xintercept = 12, size = 0.1) +
  geom_hline(yintercept = 0, size = 0.1) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Strain, Par_ue, O2_uM), rows = vars(Photoperiod, WL)) +
  theme_bw()

DielLightGrowthPro |>
  filter(Strain == "SS120",
         WL != 530,
         O2_uM == 25,
         Par_ue %in% c(30,90,180)) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
   filter(tubedata_time <= 120) |>
  ggplot() +
  geom_point(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h), size = 0.1) +
  geom_vline(xintercept = 12, size = 0.5) +
  geom_hline(yintercept = 0, size = 0.1) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Strain, Par_ue, O2_uM), rows = vars(Photoperiod, WL)) +
  theme_bw()

DielLightGrowthPro |>
  filter(Strain == "MIT9313",
         WL != 530,
         O2_uM == 25,
         Par_ue %in% c(30,90,180)) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
   filter(tubedata_time <= 120) |>
  ggplot() +
  geom_point(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h), size = 0.1) +
  geom_vline(xintercept = 12, size = 0.1) +
  geom_hline(yintercept = 0, size = 0.1) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Strain, Par_ue, O2_uM), rows = vars(Photoperiod, WL)) +
  theme_bw()

DielLightGrowthPro |>
  filter(WL == 450,
         O2_uM == 25,
         Par_ue %in% c(90)) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
   filter(tubedata_time <= 120) |>
  ggplot() +
  geom_point(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h), size = 0.1) +
  geom_vline(xintercept = 12, size = 0.1) +
  geom_hline(yintercept = 0, size = 0.1) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Strain, Par_ue, O2_uM), rows = vars(Photoperiod, WL)) +
  theme_bw()

DielLightGrowthPro |>
  filter(WL == 450,
         O2_uM == 25,
         Par_ue %in% c(90),
         Photoperiod != 4) %>% 
   unnest(cols = c(tubedata),names_sep = "_", keep_empty = TRUE) |>
  filter(tubedata_time >= 24) |>
   filter(tubedata_time <= 120) |>
  ggplot() +
  geom_point(aes(x = tubedata_ToD, y = tubedata_mu_Averh, colour = tubedata_Actinic_umolphotonsm2h), size = 0.1) +
  geom_vline(xintercept = 12, size = 0.1) +
  geom_hline(yintercept = 0, size = 0.1) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Strain, Par_ue, O2_uM), rows = vars(Photoperiod, WL)) +
  theme_bw()

```



```{r save hourly growth}
  # saveRDS(object = DielLightGrowthPro, file = file.path(DataOut, "DielLightGrowthPro.Rds"), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```

