---
title: "DielLightGrowthSVR"
author:
- Douglas A. Campbell
- Sylwia Wilczewska-Wilinska
- Mireille Savoie
date: "`r format(Sys.Date())`"
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---
# Introduction - this is a skeleton

# This  Rmd loads previously generated estimates of hourly growth and diel cumulative photon dose to cultures grown in  PSI MC.
 
# It generates Support Vector Regression trend lines.
  
# Set Options

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r libraries}
library(tidyverse)
library(zoo)

library(e1071)
library(gcookbook)  # Load gcookbook for the uspopage data set
#library(viridis)  # Load viridis for the viridis palette
library("RColorBrewer")
```

```{r colour setting}
# Bin4_nm <- c(440, 510, 590, 660)
# Bin4Colours <- c(w_length2rgb(440), w_length2rgb(510), w_length2rgb(590), w_length2rgb(660))
# names(Bin4Colours) <- Bin4_nm
```

```{r set project variables}
Project <- "PicoDiel"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedMCDielLightData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

## Chl and Cell calibrations

```{r chl and cell calibrations}
# ChlCellCalib <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData", "PicoDiel_Imported_CrossCalibrationData.Rds"))

test <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData", "PicoDiel_Tab_MDPicoMCODCorrelation.Rds"))
```




## Read Data

XXXXX

------------------------------# Support Vector regression---------------------------------------------------

https://www.geeksforgeeks.org/support-vector-regression-svr-using-linear-and-non-linear-kernels-in-scikit-learn/

https://minimatech.org/non-linear-regression-with-r/

# Support Vector regression

```{r}
MCDataHourSVR <- MCDataHour %>%
  select(c(time, ToD, Day, mu_Averh, Actinic_umolphotonsm2h,  SampleID, Strain, Tube, Run, Par_ue, Photoperiod, OD720, OD680, deltaOD, Actinic_par, WL, O2)) %>%
  drop_na(mu_Averh) %>% 
  drop_na(Actinic_umolphotonsm2h)


# Function to train an SVM model and make predictions
train_and_predict_svm <- function(data) {
  svr_model <- svm(mu_Averh ~ time, data = data, kernel = 'radial',
                   cost = 24, gamma = 100)
  data$svr_pred <- predict(svr_model, data)
  return(data)
}

# Group by Tube, train SVM model, and make predictions within each group
MCDataHourSVR <- MCDataHourSVR %>%
  group_by(Tube, Run) %>%
  nest() %>%
  mutate(data = map(data, train_and_predict_svm)) %>%
  unnest(data) %>%
  ungroup()

# Calculate the root mean squared error for each group
RMSE_by_Tube <- MCDataHourSVR %>%
  group_by(Tube, Run) %>%
  summarise(RMSE = sqrt(mean((mu_Averh - svr_pred)^2)))

```


# Save Rds for further analysis

```{r save rds}
# saveRDS(MCImportAll, file.path(DataOut, paste(Project, "Processed_MCDielLightData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(MCDataHourSVR)
```

# Create preliminary plot

```{r}
MCDataHourSVR %>%
  filter(Par_ue == 300) %>%
  filter(Photoperiod == 16) %>%
  ggplot() +
  geom_point(aes(x = time, y = mu_Averh), alpha = 0.4) +
  geom_line(aes(x = time, y = svr_pred, color = 'SVR_radial')) +
  geom_line(aes(x = time, y = mu_Averh)) +
    geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 2 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 3 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 4 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 5 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 6 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 8 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 9 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") +
  facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
  theme_bw()

MCDataHourSVR %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  #filter(Strain == "BA127R") %>% 
  ggplot() +
  geom_point(aes(x = time, y = mu_Averh), alpha = 0.4) +
  geom_line(aes(x = time, y = svr_pred, color = 'SVR_radial'), size = 1.3) +
  geom_line(aes(x = time, y = mu_Averh)) +
    geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 2 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 3 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 4 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 5 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 6 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 8 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 9 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
  theme_bw()
```


# Add facets labels and change strain name to create plot

```{r add facets labels and change strain names}
# MCImportAll$facetsPar_ue = factor(MCImportAll$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
# MCImportAll$facetsPhotoperiod = factor(MCImportAll$WL, labels = c("Photoperiod~(h)"))
# 
# MCImportAll <- MCImportAll %>% 
#   filter(Strain == "BA127R" | Strain == "BA48R" | Strain == "BA56G" | Strain == "BA77G") %>% 
#   mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
#          Strain=="BA48R"~"PE-rich_048",
#         Strain=="BA56G"~"PC-rich_056",
#          Strain=="BA77G"~"PC-rich_077")) 
```

# Create preliminary plot

```{r warning = FALSE}
#https://jmsallan.netlify.app/blog/the-brewer-palettes/
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(10))

# MCImportAll %>%
#   filter(time<250) %>% 
#   filter(time>70) %>% 
#   filter(Par_ue == 300) %>% 
#   filter(Photoperiod == 12) %>% 
#   filter(Strain == "PC-rich_077") %>% 
#   ggplot() +
#   #geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
#   geom_point(aes(x = time, y = mu_Averh, colour = Actinic_photonsm2h), alpha = 0.9) +
#   #geom_line(aes(x = time, y = svr_pred), color = 'blue', size = 0.7) +
#   geom_line(aes(x = time, y = mu_Averh)) +
#   sc +
#   facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
#   theme_bw()

```



# Create preliminary plot

```{r warning = FALSE}
#https://jmsallan.netlify.app/blog/the-brewer-palettes/
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(10))

# MCImportAll %>%
#   filter(Par_ue == 300) %>% 
#   filter(Photoperiod == 12) %>% 
#   filter(Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
#   ggplot() +
#   #geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
#   geom_point(aes(x = time, y = mu_Averh, colour = Actinic_photonsm2h), alpha = 0.9) +
#   geom_line(aes(x = time, y = svr_pred), color = 'blue', size = 0.7) +
#   #geom_line(aes(x = time, y = mu_deltaODwindow)) +
#   sc +
#   #scale_colour_discrete() + 
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) + 
#   facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
#   theme_bw()
# 
# 
# MCImportAll %>%
#   filter(time>70) %>% 
#   filter(Par_ue == 300) %>% 
#   filter(Photoperiod == 12) %>% 
#   filter(Strain == "PC-rich_077") %>% 
#   ggplot() +
#   #geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
#   geom_point(aes(x = time, y = mu_Averh, colour = Actinic_photonsm2h), alpha = 0.9) +
#   geom_line(aes(x = time, y = svr_pred), color = 'blue', size = 0.7) +
#   #geom_line(aes(x = time, y = mu_deltaODwindow)) +
#   sc +
#   #scale_colour_discrete() + 
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) + 
#   facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
#   theme_bw()

```




# Create GrowthCurve plot

```{r create GrowthCurve plot, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# 
# MCImportAll %>%
#   filter(Strain == "PC-rich_056") %>% 
#   # filter(time <200) %>% 
#  #filter(time >48) %>% 
#   filter(Run != 77) %>% 
#   ggplot() +
#   geom_point(aes(x = time, y = mu_Averh), colour = "seagreen4", alpha = 0.2, show.legend = T) +
#   geom_line(aes(x = time, y = svr_pred, colour = as.factor(Strain)), size = 0.6, show.legend = F) +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) +
#   scale_colour_discrete(type=c("blue"), name="") +
#   scale_y_continuous(breaks=seq(-0.5, 0.5, by = 0.25)) +
#   coord_cartesian(ylim = c(-0.5, 0.5)) +
#   #labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.98),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=11))
```



# Create GrowthCurve plot

```{r create GrowthCurve plot, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# 
# MCImportAll %>%
#   filter(Strain == "PC-rich_077") %>% 
#   # filter(time <200) %>% 
#  #filter(time >48) %>% 
#   filter(Run != 77) %>% 
#   ggplot() +
#   geom_point(aes(x = time, y = mu_Averh), colour = "palegreen3", alpha = 0.2, show.legend = T) +
#   geom_line(aes(x = time, y = svr_pred, colour = as.factor(Strain)), size = 0.6, show.legend = F) +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) +
#   scale_colour_discrete(type=c("blue"), name="") +
#   scale_y_continuous(breaks=seq(-0.5, 0.5, by = 0.25)) +
#   coord_cartesian(ylim = c(-0.5, 0.5)) +
#   #labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.98),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=11))
```


# Create GrowthCurve plot

```{r create GrowthCurve plot, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# 
# MCImportAll %>%
#   filter(Strain == "PE-rich_048") %>% 
#   # filter(time <200) %>% 
#  #filter(time >48) %>% 
#   filter(Run != 77) %>% 
#   ggplot() +
#   geom_point(aes(x = time, y = mu_Averh), colour = "brown1", alpha = 0.2, show.legend = T) +
#   geom_line(aes(x = time, y = svr_pred, colour = as.factor(Strain)), size = 0.6, show.legend = F) +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) +
#   scale_colour_discrete(type=c("blue"), name="") +
#   scale_y_continuous(breaks=seq(-0.5, 0.5, by = 0.25)) +
#   coord_cartesian(ylim = c(-0.5, 0.5)) +
#   #labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.98),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=11))
```

