---
title: "Import_CrossCalibrationData"
author:
- Sylwia Sliwinska-Wilczewska
- Mireille Savoie
- Naaman M. Omar 
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Import_CrossCalibrationData.Rmd imports: 
Chl Turner data from google sheet catalog (include: SySl, MiSa, JuNa), 
MDPico data from MDPico.zip folder (GitHub\BalticPhotoperiod\Data\RawData), and 
GrowthCurveData from BalticPhotoperiod_Processed_GrowthCurve.Rds (from BalticPhotoperiod)
and stored in XXX folder as: XXX.Rds

The tables with the compiled calibrations could be saved if needed (MDPicoGrowthCorrelation and TurnerGrowthCorrelation_Delta)

# Load libraries

```{r load libraries}
library(kableExtra)
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(dplyr)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)
library(ggspectra)
library(ggpubr)
library(caret)
library(gcookbook)
library(scales)
```

# Set Project Variables

```{r set project variables}
Project <- "PicoDiel"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData")

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")
RDSTablePath <- file.path("..", "Output", "TablesRDS")
```


------------------------------------------------ MetaData Catalog ------------------------------------------------------

# Read MetaData Catalog

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```

-------------------------------------- OD from MC (from growth curve) -----------------------------------------

# IMPORT GROWTH CURVE DATA FOR CORRELATION
(GrowthCurve already contain mean OD per h)

# Set project variables

```{r set project variables}
Project <- "PicoDiel"
DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthCurveData")
DataOut <- file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData")
```

# List Growth curve Rds

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```
# Read Growth curve Rds

```{r read ProcessFile Sol}
GrowthCurveFile <- "../Data/ProcessedData/ProcessedGrowthCurveData/PicoDiel_Processed_GrowthCurve.Rds"  
GrowthCurveFileName <- str_split(string = GrowthCurveFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

GrowthCurve <- readRDS(GrowthCurveFile)  %>%
  ungroup()
```


------------------------------------------------ Chla Turner ------------------------------------------------------
# Load Turner catalog

```{r load turner catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
ChlData<- read_sheet("https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0")

as.data.frame(ChlData)
ChlData <- ChlData 

ChlData <- ChlData %>%  
  mutate(TurChl_ugL = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept)) %>% 
  mutate(DATE = ymd(`DATE`)) %>% 
  rename(SampleID=CultureID) %>% 
  rename(ObsDate=DATE) %>% 
  select(c(SampleID, ObsDate, TurChl_ugL, TIME)) %>% 
  filter(TurChl_ugL<2500)  #outliers

```

# Prepare ObsTime_count to match with MC ToD data

```{r}
ChlData<-ChlData %>% 
    filter(str_detect(SampleID, "SySl")) %>% 
  mutate(TIME2 = as.POSIXct(strptime(TIME, format = "%H%M%S")),
         ToD = format(TIME2, "%H")) %>% 
  select(-c(TIME2)) %>% 
  mutate(ToD=as.double(ToD))
```

# Calculate Chl mean from 3 technical replica

```{r, warning = FALSE}
ChlData <- ChlData %>%
  group_by(SampleID, ObsDate) %>%
  summarize(SampleID, ObsDate, TurChl_ugL, TIME, ToD,
            meanTurChl_ugL = mean(TurChl_ugL),
            sdTurChl_ugL = sd(TurChl_ugL)) %>%
  ungroup()
```

# Merge ChlData with CultureCatalog

```{r, warning = FALSE, echo=FALSE}
ChlDataMeta <- CultureCatalog %>%
  full_join(., ChlData, by = c("SampleID" = "SampleID")) 

ChlDataMeta <- ChlDataMeta %>%
group_by(SampleID) %>%
  arrange(ObsDate) %>%
  mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
ungroup() %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) %>% 
  drop_na(E_days)  

```


# Merge Turner and MC OD (Growth Curve) data

```{r, warning = FALSE, echo=FALSE}

GrowthCurveTurner <- GrowthCurve %>%
  full_join(., ChlDataMeta, by = c("ToD" = "ToD", "SampleID" = "SampleID", "E_days"="E_days", "Strain"="Strain","Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "Run" = "Run", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpDate" = "ExpDate", "ExpEndDate" = "ExpEndDate")) %>% 
  drop_na(TurChl_ugL) %>% 
  filter(meanDeltaOD_h>0.02) # filter negative values and few outliers
```

# I filtered 600 and 900 uE, b/c correlation look much better without them

```{r}
GrowthCurveTurner<-GrowthCurveTurner %>% 
  filter(Par_ue != 600 & Par_ue != 900)
```


# Create preliminary plots

```{r preliminary plots}

GrowthCurveTurner %>%
  ggplot() +
  geom_point(aes(x = meanDeltaOD_h, y = TurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()
```

Pearson Correlation Coefficient and Linear Regression and coefficient of determination or R²
https://www.datacamp.com/tutorial/linear-regression-R

# Calculate Pearson correlation for cell count (MD Pico) vs OD720 (MC)

```{r}
CorrDeltaTur <- GrowthCurveTurner %>% 
  filter(TurChl_ugL<1000) %>% 
  filter(meanDeltaOD_h>0.04) %>% 
  filter(Strain == "PC-rich_056")
my_dataDeltaOD<- CorrDeltaTur
ggscatter(my_dataDeltaOD, x = "meanDeltaOD_h", y = "TurChl_ugL", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataDeltaOD
lmDeltaOD = lm(TurChl_ugL~meanDeltaOD_h, data = my_dataDeltaOD)
summary(lmDeltaOD)
# NmL = (DeltaOD*3822.21)-48.71
# Adjusted R-squared: 0.8527
# R=0.92; p=21.1e-15

CorrDeltaTur <- GrowthCurveTurner %>% 
  filter(TurChl_ugL<1500) %>% 
  filter(meanDeltaOD_h>0.03) %>% 
  filter(Strain == "PC-rich_077")
my_dataDeltaOD<- CorrDeltaTur
ggscatter(my_dataDeltaOD, x = "meanDeltaOD_h", y = "TurChl_ugL", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataDeltaOD
lmDeltaOD = lm(TurChl_ugL~meanDeltaOD_h, data = my_dataDeltaOD)
summary(lmDeltaOD)
# NmL = (DeltaOD*16779.68)+3.837
# Adjusted R-squared: 0.5892
# R=0.77; p=2e-10


CorrDeltaTur <- GrowthCurveTurner %>% 
  filter(TurChl_ugL<1000) %>% 
  filter(meanDeltaOD_h>0.03) %>% 
  filter(Strain == "PE-rich_048")
my_dataDeltaOD<- CorrDeltaTur
ggscatter(my_dataDeltaOD, x = "meanDeltaOD_h", y = "TurChl_ugL", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataDeltaOD
lmDeltaOD = lm(TurChl_ugL~meanDeltaOD_h, data = my_dataDeltaOD)
summary(lmDeltaOD)
# NmL = (DeltaOD*4328.492)+144.24
# Adjusted R-squared: 0.5508
# R=0.74; p=3.9e-11


CorrDeltaTur <- GrowthCurveTurner %>% 
  filter(TurChl_ugL<1200) %>% 
  filter(meanDeltaOD_h>0.05) %>% 
  filter(Strain == "PE-rich_127") 
my_dataDeltaOD<- CorrDeltaTur
ggscatter(my_dataDeltaOD, x = "meanDeltaOD_h", y = "TurChl_ugL", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataDeltaOD
lmDeltaOD = lm(TurChl_ugL~meanDeltaOD_h, data = my_dataDeltaOD)
summary(lmDeltaOD)
# NmL = (DeltaOD*2805.1)+183.9
# Adjusted R-squared: 0.4941
# R=0.7; p = 2.1e-07

```

# Create table with Pearson correlation and preliminary plot (Turner vs MC DeltaOD)

```{r}
data_textPaersonBA56G_720 <- data.frame(Linear_regression = c('µg Chl a/L) = (DeltaOD*3822.21)-48.71'), Strain = c("PC-rich_056"), OD = c("720"), R_square = c(0.8527), R = c(0.92), p_value = c(0))
data_textPaersonBA77G_720 <- data.frame(Linear_regression = c('µg Chl a/L = (DeltaOD*16779.68)+3.837'), Strain = c("PC-rich_077"), OD = c("720"), R_square = c(0.5892), R = c(0.77), p_value = c(0))
data_textPaersonBA48R_720 <- data.frame(Linear_regression = c('µg Chl a/L = (DeltaOD*4328.492)+144.24'), Strain = c("PE-rich_048"), OD = c("720"), R_square = c(0.5508), R = c(0.74), p_value = c(0))
data_textPaersonBA127R_720 <- data.frame(Linear_regression = c('µg Chl a/L = (DeltaOD*2805.1)+183.9'), Strain = c("PE-rich_127"), OD = c("720"), R_square = c(0.4941), R = c(0.70), p_value = c(0))

TurnerGrowthCorrelation_Delta<-rbind(data_textPaersonBA56G_720, data_textPaersonBA77G_720, data_textPaersonBA48R_720, data_textPaersonBA127R_720)

GrowthCurveTurner %>% 
  filter(TurChl_ugL<1000) %>% 
  filter(meanDeltaOD_h>0.04) %>% 
  filter(Strain == "PC-rich_056") %>% 
  ggplot(aes(x = meanDeltaOD_h, y = TurChl_ugL)) +
  geom_point(aes(x = meanDeltaOD_h, y = TurChl_ugL), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA56G_720, aes(x=0.06, y=10000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  #labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

GrowthCurveTurner %>% 
  filter(TurChl_ugL<1500) %>% 
  filter(meanDeltaOD_h>0.03) %>% 
  filter(Strain == "PC-rich_077") %>% 
  ggplot(aes(x = meanDeltaOD_h, y = TurChl_ugL)) +
  geom_point(aes(x = meanDeltaOD_h, y = TurChl_ugL), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA77G_720, aes(x=0.06, y=10000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  #labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

GrowthCurveTurner %>% 
  filter(TurChl_ugL<1000) %>% 
  filter(meanDeltaOD_h>0.03) %>% 
  filter(Strain == "PE-rich_048") %>% 
  ggplot(aes(x = meanDeltaOD_h, y = TurChl_ugL)) +
  geom_point(aes(x = meanDeltaOD_h, y = TurChl_ugL), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA48R_720, aes(x=0.06, y=10000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  #labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

GrowthCurveTurner %>% 
  filter(TurChl_ugL<1200) %>% 
  filter(meanDeltaOD_h>0.05) %>% 
  filter(Strain == "PE-rich_127") %>% 
  ggplot(aes(x = meanDeltaOD_h, y = TurChl_ugL)) +
  geom_point(aes(x = meanDeltaOD_h, y = TurChl_ugL), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA127R_720, aes(x=0.06, y=10000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  #labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

rm(data_textPaersonBA56G_720, data_textPaersonBA77G_720, data_textPaersonBA48R_720, data_textPaersonBA127R_720)
```
# Cleaning the environment

```{r}
rm(lmDeltaOD, my_dataDeltaOD, ChlDataMeta, CorrDeltaTur)
```


# Save RDS that create stats and tables

```{r save rds}
# saveRDS(TurnerGrowthCorrelation_Delta, file.path(RDSTablePath, paste(Project, "Tab_TurnerDeltaODCorrelation.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(TurnerGrowthCorrelation_Delta, file.path(DataOut, paste(Project, "Tab_TurnerDeltaODCorrelation.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


--------------------------------------------------- MD Pico --------------------------------------------

# IMPORT MD PICO CORRELATION DATA

```{r set project variables, warning = FALSE, echo = FALSE}
Project <- "PicoDiel"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedCrossCalibrationData")
zip_file <- file.path("..", "Data", "RawData", "MDPico.zip")

# List files in the extracted folder with a ".txt" extension
CountFiles <- unzip(zip_file, list = TRUE)
CountFiles <- CountFiles[grepl(".csv$", CountFiles$Name), "Name"]
print(CountFiles)

FileID <- "ExperimentSummaryData"
FileEncode <- "UTF-8" 
HeaderRows <- 0
DelimCS <- ","
```

# Read fread_plus function

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
# Define function to read and process each file
fread_plus <- function(Flnm, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)
  
  # Read the file using read.table
  data <- read.table(con, skip = HeaderRows, encoding = FileEncode, sep = Delim, header = TRUE)
  
  # Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })
  
  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

# Use map_df to read and process all files in CountFiles
MDPicoTidy <- CountFiles %>%
  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = DelimCS))
```

```{r tidy CountTidy}

MDPicoTidy <- MDPicoTidy %>% 
  select(-c("Concentration", "Group", "Compound", "CDateTime")) %>% # remove superfluous columns
  mutate(Filename = str_remove(string = Filename, pattern = ".csv")) %>%
  mutate(Filename = str_remove(string = Filename, pattern = "../MDPico/")) %>%
  separate(Filename, into = c("ObsDate", "Project", "Initials",  "PlateNr", "IndStud", "Organism", "Count"), sep = "([\\/\\/\\_\\_\\_\\_\\_])", remove = FALSE) %>%
  select(-c("IndStud", "Organism", "Count")) %>% 
  mutate(ObsDate = ymd_hm(ObsDate)) 
```

# Load MDPicoMetaData catalog

```{r load local metadatacatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# this is the URL or ID of a Sheet readable by anyone (with a link)

MDPicoMetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1Lerp5u25kzBtaBbnOYElYqUP59cn68gJpxxayhnGdkw/edit#gid=0") %>%
  #mutate(Date = as.numeric(Date)) %>%
  mutate(Date = ymd_hm(`Date`)) %>%
  separate(Date, into = c("Date_count", "Time_count"), sep = " ", remove = FALSE) %>%
  mutate(Date_count = ymd(`Date_count`)) 
```


# Merge MD Pico and Culture catalog

```{r}
MDPicoMeta <- MDPicoMetaData %>%
  left_join(., CultureCatalog, by = c("SampleID" = "SampleID")) %>% 
  drop_na(Strain)
```

# check if I do not lost some data!

```{r}
MDPicoAll <- MDPicoTidy %>%
  mutate(PlateNr = as.double(PlateNr)) %>%
  left_join(., MDPicoMeta, by = c("Well.Name" = "WellNumber", "PlateNr" = "PlateNumber")) %>% 
  drop_na(Strain)
```

```{r, warning = FALSE}
MDPicoAll <- MDPicoAll %>%
  mutate(culture_inocul_L = as.double(culture_inocul_L)) %>%
  mutate(CapAreaPercentage = as.double(CapAreaPercentage)) %>%

  mutate(CellmL_MDPico = (`Cell.Count` * (0.001/culture_inocul_L)) /(CapAreaPercentage/100)) %>%
  # mutate(cellsml = `cellsmlwithoutpercentage`/(CapAreaPercentage/100))
group_by(Date, SampleID) %>%

summarize(Well.Name, Cell.Count, Filename, ObsDate, PlateNr, PlateID, SampleID, Date, Date_count, Time_count, media_inocul_L, culture_inocul_L, CapAreaPercentage, Run, Strain, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, Tube, O2, WL, LightShape, ExpEndDate, CellmL_MDPico, meanCellmL_MDPico = mean(CellmL_MDPico), sdCellmL_MDPico = sd(CellmL_MDPico)) %>%

ungroup() %>%
  
group_by(SampleID) %>%
  arrange(Date_count) %>%
  mutate(E_days = as.numeric((Date_count - ExpDate[1]))) %>%
ungroup() %>% 
  rename(Cell_Count=Cell.Count) %>% 
  rename(Well_Name=Well.Name) %>% 
  rename(MeasDate = ObsDate) %>% 
  rename(ObsDateTime = Date) %>% 
  rename(ObsDate_count = Date_count) %>% 
  rename(ObsTime_count = Time_count) %>% 
  rename(FilenameMDPico=Filename)  
```

# Create Preliminary plot

```{r preliminary plot}
MDPicoAll %>%
  ggplot() +
  geom_point(aes(x = E_days, y = meanCellmL_MDPico)) +
  # scale_x_continuous(breaks=seq(0, 14, by = 7)) +
  # coord_cartesian(xlim = c (-1, 15)) +
  ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Strain, Photoperiod), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()
```

# Removing unrevelant column

```{r}
#colnames(MDPicoAll)
MDPicoAll <- MDPicoAll %>%
  select(-c(MeasDate, PlateNr, PlateID, Well_Name, media_inocul_L, culture_inocul_L, CapAreaPercentage)) %>% 
  drop_na(Cell_Count)
```

# Cleaning the environment

```{r}
rm(CultureCatalog, MDPicoMeta, MDPicoMetaData, MDPicoTidy)
```

# Save rds for further analysis if needed

```{r save rds}
# saveRDS(MDPicoAll, file.path(DataOut, paste(Project, "Imported_MDPicoData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```



-------------------------------------# MD Pico vs. MC OD (Growth Curve) correlation ---------------------------------------

# Prepare ObsTime_count to match with MC ToD data

```{r}
MDPicoAll<-MDPicoAll %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) %>% 
  mutate(ObsTime_count=as.character(ObsTime_count))
  
MDPicoAll$ToD<-gsub("([0-9]+):.*", "\\1", MDPicoAll$ObsTime_count)

MDPicoAll<-MDPicoAll %>% 
  mutate(ToD=as.double(ToD))
```

# Merge MD Pico and MC OD (Growth Curve) data

```{r, warning = FALSE, echo=FALSE}
MCMDPicoCorr <- GrowthCurve %>%
  full_join(., MDPicoAll, by = c("ToD" = "ToD", "SampleID" = "SampleID", "E_days"="E_days", "Strain"="Strain","Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "Run" = "Run", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpDate" = "ExpDate", "ExpEndDate" = "ExpEndDate"))  %>% 
  drop_na(meanOD680_h) %>% 
  drop_na(Cell_Count)
```

# Create preliminary plots

```{r preliminary plots}

MCMDPicoCorr %>%
  ggplot() +
  geom_point(aes(x = meanOD680_h, y = CellmL_MDPico)) +
  #labs(y = "Number of cells (N/mL)", x = "Absorbance" ~ "("~OD[750]~")") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

MCMDPicoCorr %>%
  ggplot() +
  geom_point(aes(x = meanOD720_h, y = CellmL_MDPico)) +
  #labs(y = "Number of cells (N/mL)", x = "Absorbance" ~ "("~OD[750]~")") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

MCMDPicoCorr %>%
  ggplot() +
  geom_point(aes(x = meanDeltaOD_h, y = CellmL_MDPico)) +
  #labs(y = "Number of cells (N/mL)", x = "Absorbance" ~ "("~OD[750]~")") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()
```

Pearson Correlation Coefficient and Linear Regression and coefficient of determination or R²
https://www.datacamp.com/tutorial/linear-regression-R

# Calculate Pearson correlation for cell count (MD Pico) vs OD720 (MC)

```{r}
CorrCleanOD720 <- MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_056")
my_dataOD720<- CorrCleanOD720
ggscatter(my_dataOD720, x = "meanOD720_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD720
lmOD720 = lm(CellmL_MDPico~meanOD720_h, data = my_dataOD720)
summary(lmOD720)
# NmL = (OD720*199514099)+5596282
# Adjusted R-squared: 0.5312
# R=0.73; p=3.9e-16

CorrCleanOD720 <- MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_077")
my_dataOD720<- CorrCleanOD720
ggscatter(my_dataOD720, x = "meanOD720_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD720
lmOD720 = lm(CellmL_MDPico~meanOD720_h, data = my_dataOD720)
summary(lmOD720)
# NmL = (OD720*214694020)+31010844
# Adjusted R-squared: 0.7894
# R=0.89; p=2.2e-16


CorrCleanOD720 <- MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_048")
my_dataOD720<- CorrCleanOD720
ggscatter(my_dataOD720, x = "meanOD720_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD720
lmOD720 = lm(CellmL_MDPico~meanOD720_h, data = my_dataOD720)
summary(lmOD720)
# NmL = (OD720*216637133)+60707950
# Adjusted R-squared: 0.4508
# R=0.67; p=1.7e-11


CorrCleanOD720 <- MCMDPicoCorr %>% 
  filter(CellmL_MDPico>0.3e08) %>% 
  filter(Strain == "PE-rich_127") 
my_dataOD720<- CorrCleanOD720
ggscatter(my_dataOD720, x = "meanOD720_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD720
lmOD720 = lm(CellmL_MDPico~meanOD720_h, data = my_dataOD720)
summary(lmOD720)
# NmL = (OD720*151131397)+79519260
# Adjusted R-squared: 0.4035
# R=0.64; p = 2.7e-09

```

# Calculate Pearson correlation for cell count (MD Pico) vs OD680 (MC)

```{r}
CorrCleanOD680 <- MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_056")
my_dataOD680<- CorrCleanOD680
ggscatter(my_dataOD680, x = "meanOD680_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD680
lmOD680 = lm(CellmL_MDPico~meanOD680_h, data = my_dataOD680)
summary(lmOD680)
# NmL = (OD680*159866357)+3667252
# Adjusted R-squared: 0.5344
# R=0.73; p=2.8e-16

CorrCleanOD680 <- MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_077")
my_dataOD680<- CorrCleanOD680
ggscatter(my_dataOD680, x = "meanOD680_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD680
lmOD680 = lm(CellmL_MDPico~meanOD680_h, data = my_dataOD680)
summary(lmOD680)
# NmL = (OD680*174836861)+27696294
# Adjusted R-squared: 0.8286
# R=0.91; p=2.2e-16


CorrCleanOD680 <- MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_048")
my_dataOD680<- CorrCleanOD680
ggscatter(my_dataOD680, x = "meanOD680_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD680
lmOD680 = lm(CellmL_MDPico~meanOD680_h, data = my_dataOD680)
summary(lmOD680)
# NmL = (OD680*195634847)+50753022
# Adjusted R-squared: 0.5202
# R=0.72; p=9.5e-14


CorrCleanOD680 <- MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_127") %>% 
  filter(CellmL_MDPico>0.3e08) 
my_dataOD680<- CorrCleanOD680
ggscatter(my_dataOD680, x = "meanOD680_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD680
lmOD680 = lm(CellmL_MDPico~meanOD680_h, data = my_dataOD680)
summary(lmOD680)
# NmL = (OD680*124907790)+77641680
# Adjusted R-squared: 0.4242
# R=0.65; p = 7.7e-10
```

# Create table with Pearson correlation and preliminary plot (MD Pico vs MC OD720)

```{r}
data_textPaersonBA56G_720 <- data.frame(Linear_regression = c('N/mL = (OD720*199514099)+5596282'), Strain = c("PC-rich_056"), OD = c("720"), R_square = c(0.5312), R = c(0.73), p_value = c(0))
data_textPaersonBA77G_720 <- data.frame(Linear_regression = c('N/mL = (OD720*214694020)+31010844'), Strain = c("PC-rich_077"), OD = c("720"), R_square = c(0.7894), R = c(0.89), p_value = c(0))
data_textPaersonBA48R_720 <- data.frame(Linear_regression = c('N/mL = (OD720*216637133)+60707950'), Strain = c("PE-rich_048"), OD = c("720"), R_square = c(0.4508), R = c(0.67), p_value = c(0))
data_textPaersonBA127R_720 <- data.frame(Linear_regression = c('N/mL = (OD720*151131397)+79519260'), Strain = c("PE-rich_127"), OD = c("720"), R_square = c(0.4035), R = c(0.64), p_value = c(0))

MDPicoGrowthCorrelation_720<-rbind(data_textPaersonBA56G_720, data_textPaersonBA77G_720, data_textPaersonBA48R_720, data_textPaersonBA127R_720)

MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_056") %>% 
  ggplot(aes(x = meanOD720_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD720_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA56G_720, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_077") %>% 
  ggplot(aes(x = meanOD720_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD720_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA77G_720, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_048") %>% 
  ggplot(aes(x = meanOD720_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD720_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA48R_720, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_127") %>% 
  filter(CellmL_MDPico>0.3e08) %>% 
  ggplot(aes(x = meanOD720_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD720_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA127R_720, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

rm(data_textPaersonBA56G_720, data_textPaersonBA77G_720, data_textPaersonBA48R_720, data_textPaersonBA127R_720)
```

# Create table with Pearson correlation and preliminary plot (MD Pico vs MC OD680)

```{r}

data_textPaersonBA56G_680 <- data.frame(Linear_regression = c('N/mL = (OD680*159866357)+3667252'), Strain = c("PC-rich_056"), OD = c("680"), R_square = c(0.5344), R = c(0.73), p_value = c(0))
data_textPaersonBA77G_680 <- data.frame(Linear_regression = c('N/mL = (OD680*174836861)+27696294'), Strain = c("PC-rich_077"), OD = c("680"), R_square = c(0.82864), R = c(0.91), p_value = c(0))
data_textPaersonBA48R_680 <- data.frame(Linear_regression = c('N/mL = (OD680*195634847)+50753022'), Strain = c("PE-rich_048"), OD = c("680"), R_square = c(0.5202), R = c(0.72), p_value = c(0))
data_textPaersonBA127R_680 <- data.frame(Linear_regression = c('N/mL = (OD680*124907790)+77641680'), Strain = c("PE-rich_127"), OD = c("680"), R_square = c(0.4242), R = c(0.65), p_value = c(0))

MDPicoGrowthCorrelation_680<-rbind(data_textPaersonBA56G_680, data_textPaersonBA77G_680, data_textPaersonBA48R_680, data_textPaersonBA127R_680)


MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_056") %>% 
  ggplot(aes(x = meanOD680_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD680_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA56G_680, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (OD680 nm)") +
  theme_bw() 

MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_077") %>% 
  ggplot(aes(x = meanOD680_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD680_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA77G_680, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (OD680 nm)") +
  theme_bw()

MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_048") %>% 
  ggplot(aes(x = meanOD680_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD680_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA48R_680, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (OD680 nm)") +
  theme_bw() 

MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_127") %>% 
  filter(CellmL_MDPico>0.3e08) %>% 
  ggplot(aes(x = meanOD680_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD680_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA127R_680, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (OD680 nm)") +
  theme_bw() 

rm(data_textPaersonBA56G_680, data_textPaersonBA77G_680, data_textPaersonBA48R_680, data_textPaersonBA127R_680)
```

# Create table with equations obtained from Pearson correlation (for calculate number of cells based on OD)

```{r}
MDPicoGrowthCorrelation<-rbind(MDPicoGrowthCorrelation_680, MDPicoGrowthCorrelation_720)

rm(MDPicoGrowthCorrelation_680, MDPicoGrowthCorrelation_720)
```

# Save RDS that create stats and tables

```{r save rds}
# saveRDS(MDPicoGrowthCorrelation, file.path(RDSTablePath, paste(Project, "Tab_MDPicoMCODCorrelation.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(MDPicoGrowthCorrelation, file.path(DataOut, paste(Project, "Tab_MDPicoMCODCorrelation.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Cleaning the environment

```{r}
rm(lmOD680, lmOD720, CorrCleanOD720, CorrCleanOD680, my_dataOD680, my_dataOD720)
```



------------------------------------------------------ESTIMATIONS --------------------------------------------------

-------------------------- Estimated ug Chl ug/L every h based on correlation from Turner -----------------------------
-------------------------- Estimated number of cells/mL every h based on correlation from MDPico -----------------------------

# Estimated number of ug Chl ug/L every h based on correlation from Turner and Estimated number of cells/mL every h based on correlation from MDPico (MDPicoGrowthCorrelation)

```{r}

MCBA56G <- GrowthCurve %>% 
filter(Strain == "PC-rich_056") %>% 
mutate(cellmL_OD680_MDPico = 159866357*meanOD680_h+3667252) %>% 
mutate(cellmL_OD720_MDPico = 199514099*meanOD680_h+5596282) %>% 
mutate(Chla_ugL_Tur = 3822.21*meanDeltaOD_h-48.71) 

MCBA77G <- GrowthCurve %>% 
filter(Strain == "PC-rich_077") %>% 
mutate(cellmL_OD680_MDPico = 174836861*meanOD680_h+27696294) %>% 
mutate(cellmL_OD720_MDPico = 214694020*meanOD680_h+31010844) %>% 
mutate(Chla_ugL_Tur = 16779.68*meanDeltaOD_h+3.837) 
  
MCBA48R <- GrowthCurve %>% 
filter(Strain == "PE-rich_048") %>% 
mutate(cellmL_OD680_MDPico = 195634847*meanOD680_h+50753022) %>% 
mutate(cellmL_OD720_MDPico = 216637133*meanOD680_h+60707950) %>% 
mutate(Chla_ugL_Tur = 2805.1*meanDeltaOD_h+183.9)

MCBA127R <- GrowthCurve %>% 
filter(Strain == "PE-rich_127") %>% 
mutate(cellmL_OD680_MDPico = 124907790*meanOD680_h+77641680) %>% 
mutate(cellmL_OD720_MDPico = 151131397*meanOD680_h+79519260) %>% 
mutate(Chla_ugL_Tur = 10316.44*meanDeltaOD_h+102.61)

GrowthCurve_All <- rbind(MCBA127R, MCBA48R, MCBA56G, MCBA77G)

GrowthCurve_All<-GrowthCurve_All %>% # estimate cell per L
mutate(cellL_OD680_MDPico=cellmL_OD680_MDPico*1000) %>% 
mutate(cellL_OD720_MDPico=cellmL_OD720_MDPico*1000)

rm(MCBA127R, MCBA48R, MCBA56G, MCBA77G)
```


# Save rds for further analysis

```{r save rds}
# saveRDS(GrowthCurve_All, file.path(DataOut, paste(Project, "Imported_CrossCalibrationData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


# Correlations from Polish flowcytometer (BD Accuri) and Polish Spec if needed

```{r}

#           Strain == 'BA77G' ~ 5766620.03*OD750+5146.44,
#          Strain == 'BA56G' ~ 815627.77*OD750-6499.89, 
#          Strain == 'BA48R' ~ 110516351.55*OD750-568505.87,
#          Strain == 'BA127R' ~ 124271003.22*OD750-1691760.02))
```


