---
title: "MCDielLight"
author:
- Douglas A. Campbell
- Sylwia Wilczewska-Wilinska
- Mireille Savoie
date: "`r format(Sys.Date())`"
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---
# Introduction

# This Rmd loads previously imported, tidied data from the PSI MC and generates estimates of hourly and diel cumulative photon dose to cultures.  It imports light response equations and calibrations for JVPSII to estimate time resolved JVPSII.

# Set Options

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r libraries}
library(tidyverse)
library(zoo)

library(e1071)
library(gcookbook)  # Load gcookbook for the uspopage data set
#library(viridis)  # Load viridis for the viridis palette
library("RColorBrewer")
```

```{r colour setting}
# Bin4_nm <- c(440, 510, 590, 660)
# Bin4Colours <- c(w_length2rgb(440), w_length2rgb(510), w_length2rgb(590), w_length2rgb(660))
# names(Bin4Colours) <- Bin4_nm
```

```{r set project variables}
Project <- "PicoDiel"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedMCDielLightData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

## JVPSII light response and calibrations
Think about how to calibrate JVPSII; what does it mean?  Use e cell-1 s-1?
```{r jvpsii}

#JVPSII_eLs_ModelTerms <- readRDS(file = file.path("..", "Data","CleanedData", "JVPSII_eLs_ModelTerms.Rds"))

Processed_Solisense_LRC <- readRDS(file = file.path("..", "Data","CleanedData", "Processed_Solisense_LRC.Rds")) |>
select(c("SampleID", "Strain", "Ex_WL",  "GRCplatt_Model", "GRCplatt_Param")) 
```


## Read Data
Check with Sylwia & Mireille about what filter(s) have been applied in 'Process' Consider using 'Process' before this step
```{r data files}
MCFiles <- list.files(path = file.path("..", "Data", "ImportedData", "ImportedMCData"), full.names = TRUE)
MCFiles
```

```{r read data}

MCData <- readRDS(file = MCFiles[1]) |>
  ungroup() |>
  mutate(deltaOD = OD680 - OD720) |>
  filter(OD720 >= 0)

  colnames(MCData)
  
MCDataAll <- map_df(MCFiles, readRDS) |>
  ungroup() |>
  mutate(deltaOD = OD680 - OD720) |>
  filter(OD720 >= 0)
```

```{r par_time_plot}
MCData |>
  ggplot() +
  geom_point(aes(x = time, y = Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
  filter(time >= 48,
         time <= 72) |>
  ggplot() +
  geom_point(aes(x = time, y = Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
  filter(time >= 48,
         time <= 72) |>
  ggplot() +
  geom_point(aes(x = time, y = deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
  filter(time >= 48,
         time <= 72) |>
  ggplot() +
  geom_point(aes(x = time, y = Actinic_par)) +
  geom_point(aes(x = time, y = 1000 * deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCData |>
  filter(Tube == 4) |>
  # filter(time >= 48,
  #        time <= 72) |>
  ggplot() +
  geom_point(aes(x = time, y = Actinic_par)) +
  geom_point(aes(x = time, y = 1000 * deltaOD, colour = WL)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()
```


#https://stackoverflow.com/questions/76603287/calculate-linear-regression-slope-with-moving-window

rollapply and rollmean not behaving as expecting.
Seeking rolling window with width of 12 rows; 5 min per row, 60 min window, outputs do not match expectations.
-why is rollapply NA for first 5 rows; why not 12 rows?;
-why are mu not as expected from manual?
  Solved with align = "right" and align = "left"
Still working on verifying cumulative photons h-1 and d-1; Verified.

```{r growth rates}

#slope <- function(x) coef(lm(x[, 2] ~ x[, 1]))[[2]] #same result, much slower
slope <- function(x) cov(x[, 1], x[, 2]) / var(x[, 1])

#FitWindow_h <- 2
#maybe issues still with changes in light level that do not align with growth measurement points

#maybe should estimate growth rates, then use 'summarize' to do sum of actinic photon dose for each hour?

ODinterval <- 5

MCDataHour <- MCDataAll |>
  group_by(Filename, Tube) |>
   mutate(Actinic_umolphotonsm2h = zoo::rollsum(Actinic_par * 60 * ODinterval , k = 60/ODinterval, fill = NA, align = "right")) |> #PAR per h
  mutate(mu_OD720window = zoo::rollapply(cbind(time, log(OD720)), width = 60/ODinterval, FUN = slope, by.column=FALSE, fill=NA, align = "right")) |> #slope
  mutate(mu_Averh = zoo::rollmean(mu_OD720window, k = 60/ODinterval, fill = NA, align = "left")) |> #average of first 12 row  ungroup() 
filter(time - round(time) == 0) #crude collapse to 1 measurement per hour

```

```{r preliminary plot}
MCDataHour |>
  filter(Run == 39) %>% 
  filter(time >= 24) |>
  #        time <= 72) |>
  #filter(time < 100) |>
  ggplot() +
  geom_point(aes(x = time, y = mu_Averh, colour = Actinic_umolphotonsm2h)) +
  geom_point(aes(x = time, y = OD720), colour = "green") +
  facet_grid(cols = vars(Tube), rows = vars(Filename)) +
  theme_bw()

```


```{r hourly plots exploration}
#temporary
#use case_when to remove 'dark' periods?
#bad to filter and only then estimate growth rates; better to do across 1 h window


MCDataHour |>
    filter(Run == 39) %>% 
    filter(time >= 24) |>
   filter(time <= 96) |>
  ggplot() +
  geom_point(aes(x = Actinic_umolphotonsm2h, y = mu_Averh, colour = ToD)) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour |>
    filter(Run == 39) %>% 
    filter(time >= 24) |>
   filter(time <= 96) |>
  ggplot() +
  geom_point(aes(x = ToD, y = mu_Averh, colour = Actinic_umolphotonsm2h)) +
  geom_line(aes(x = ToD, y = mu_Averh, colour = Actinic_umolphotonsm2h)) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour |>
    filter(Run == 39) %>% 
  filter(Tube == 4) |>
  filter(time >= 24) |>
  filter(time <= 96) |>
  ggplot() +
  geom_point(aes(x = ToD, y = mu_Averh, colour = Actinic_umolphotonsm2h)) +
  scale_color_gradient(low = "black", high = "yellow") +
  facet_grid(cols = vars(Tube)) +
  theme_bw()


MCDataHour |>
  filter(Run == 39) %>% 
  filter(time >= 24) |>
  filter(time <= 96) |>
  #filter(Actinic_par > 1) |>
  ggplot() +
  geom_point(aes(x = ToD, y = mu_Averh, colour = Actinic_umolphotonsm2h)) +
  geom_line(aes(x = ToD, y = mu_Averh, colour = Actinic_umolphotonsm2h)) +
  scale_color_gradient(low = "black", high = "yellow") +
  geom_smooth(aes(x = ToD, y = mu_Averh)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

```
# JVPSII exploration
```{r jvpsii eLs 445}
MCDataHour <- MCDataHour |>
  mutate(JVPSII_eLh = Actinic_umolphotonsm2h * JVPSII_eLs_ModelTerms$Slope[which(JVPSII_eLs_ModelTerms$Ex_WL == 445)] * 3600)
```


------------------------------# Support Vector regression---------------------------------------------------

https://www.geeksforgeeks.org/support-vector-regression-svr-using-linear-and-non-linear-kernels-in-scikit-learn/

https://minimatech.org/non-linear-regression-with-r/

# Support Vector regression

```{r}
MCDataHourSVR <- MCDataHour %>%
  select(c(time, ToD, Day, mu_Averh, Actinic_umolphotonsm2h,  SampleID, Strain, Tube, Run, Par_ue, Photoperiod, OD720, OD680, deltaOD, Actinic_par, WL, O2)) %>%
  drop_na(mu_Averh) %>% 
  drop_na(Actinic_umolphotonsm2h)


# Function to train an SVM model and make predictions
train_and_predict_svm <- function(data) {
  svr_model <- svm(mu_Averh ~ time, data = data, kernel = 'radial',
                   cost = 24, gamma = 100)
  data$svr_pred <- predict(svr_model, data)
  return(data)
}

# Group by Tube, train SVM model, and make predictions within each group
MCDataHourSVR <- MCDataHourSVR %>%
  group_by(Tube, Run) %>%
  nest() %>%
  mutate(data = map(data, train_and_predict_svm)) %>%
  unnest(data) %>%
  ungroup()

# Calculate the root mean squared error for each group
RMSE_by_Tube <- MCDataHourSVR %>%
  group_by(Tube, Run) %>%
  summarise(RMSE = sqrt(mean((mu_Averh - svr_pred)^2)))

```


# Save Rds for further analysis

```{r save rds}
# saveRDS(MCImportAll, file.path(DataOut, paste(Project, "Processed_MCDielLightData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(MCDataHourSVR)
```

# Create preliminary plot

```{r}
MCDataHourSVR %>%
  filter(Par_ue == 300) %>%
  filter(Photoperiod == 16) %>%
  ggplot() +
  geom_point(aes(x = time, y = mu_Averh), alpha = 0.4) +
  geom_line(aes(x = time, y = svr_pred, color = 'SVR_radial')) +
  geom_line(aes(x = time, y = mu_Averh)) +
    geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 2 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 3 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 4 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 5 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 6 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 8 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 9 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") +
    geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") +
  facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
  theme_bw()

MCDataHourSVR %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  #filter(Strain == "BA127R") %>% 
  ggplot() +
  geom_point(aes(x = time, y = mu_Averh), alpha = 0.4) +
  geom_line(aes(x = time, y = svr_pred, color = 'SVR_radial'), size = 1.3) +
  geom_line(aes(x = time, y = mu_Averh)) +
    geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 2 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 3 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 4 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 5 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 6 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 8 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 9 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
  theme_bw()
```


# Add facets labels and change strain name to create plot

```{r add facets labels and change strain names}
# MCImportAll$facetsPar_ue = factor(MCImportAll$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
# MCImportAll$facetsPhotoperiod = factor(MCImportAll$WL, labels = c("Photoperiod~(h)"))
# 
# MCImportAll <- MCImportAll %>% 
#   filter(Strain == "BA127R" | Strain == "BA48R" | Strain == "BA56G" | Strain == "BA77G") %>% 
#   mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
#          Strain=="BA48R"~"PE-rich_048",
#         Strain=="BA56G"~"PC-rich_056",
#          Strain=="BA77G"~"PC-rich_077")) 
```

# Create preliminary plot

```{r warning = FALSE}
#https://jmsallan.netlify.app/blog/the-brewer-palettes/
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(10))

# MCImportAll %>%
#   filter(time<250) %>% 
#   filter(time>70) %>% 
#   filter(Par_ue == 300) %>% 
#   filter(Photoperiod == 12) %>% 
#   filter(Strain == "PC-rich_077") %>% 
#   ggplot() +
#   #geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
#   geom_point(aes(x = time, y = mu_Averh, colour = Actinic_photonsm2h), alpha = 0.9) +
#   #geom_line(aes(x = time, y = svr_pred), color = 'blue', size = 0.7) +
#   geom_line(aes(x = time, y = mu_Averh)) +
#   sc +
#   facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
#   theme_bw()

```


# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_HourlyGrowthRateExample1",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Create preliminary plot

```{r warning = FALSE}
#https://jmsallan.netlify.app/blog/the-brewer-palettes/
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(10))

# MCImportAll %>%
#   filter(Par_ue == 300) %>% 
#   filter(Photoperiod == 12) %>% 
#   filter(Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
#   ggplot() +
#   #geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
#   geom_point(aes(x = time, y = mu_Averh, colour = Actinic_photonsm2h), alpha = 0.9) +
#   geom_line(aes(x = time, y = svr_pred), color = 'blue', size = 0.7) +
#   #geom_line(aes(x = time, y = mu_deltaODwindow)) +
#   sc +
#   #scale_colour_discrete() + 
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) + 
#   facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
#   theme_bw()
# 
# 
# MCImportAll %>%
#   filter(time>70) %>% 
#   filter(Par_ue == 300) %>% 
#   filter(Photoperiod == 12) %>% 
#   filter(Strain == "PC-rich_077") %>% 
#   ggplot() +
#   #geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
#   geom_point(aes(x = time, y = mu_Averh, colour = Actinic_photonsm2h), alpha = 0.9) +
#   geom_line(aes(x = time, y = svr_pred), color = 'blue', size = 0.7) +
#   #geom_line(aes(x = time, y = mu_deltaODwindow)) +
#   sc +
#   #scale_colour_discrete() + 
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) + 
#   facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
#   theme_bw()

```

# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_HourlyGrowthRateExample2",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```


# Create GrowthCurve plot

```{r create GrowthCurve plot, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# 
# MCImportAll %>%
#   filter(Strain == "PC-rich_056") %>% 
#   # filter(time <200) %>% 
#  #filter(time >48) %>% 
#   filter(Run != 77) %>% 
#   ggplot() +
#   geom_point(aes(x = time, y = mu_Averh), colour = "seagreen4", alpha = 0.2, show.legend = T) +
#   geom_line(aes(x = time, y = svr_pred, colour = as.factor(Strain)), size = 0.6, show.legend = F) +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) +
#   scale_colour_discrete(type=c("blue"), name="") +
#   scale_y_continuous(breaks=seq(-0.5, 0.5, by = 0.25)) +
#   coord_cartesian(ylim = c(-0.5, 0.5)) +
#   #labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.98),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_HourlyGrowthRate_056",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```


# Create GrowthCurve plot

```{r create GrowthCurve plot, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# 
# MCImportAll %>%
#   filter(Strain == "PC-rich_077") %>% 
#   # filter(time <200) %>% 
#  #filter(time >48) %>% 
#   filter(Run != 77) %>% 
#   ggplot() +
#   geom_point(aes(x = time, y = mu_Averh), colour = "palegreen3", alpha = 0.2, show.legend = T) +
#   geom_line(aes(x = time, y = svr_pred, colour = as.factor(Strain)), size = 0.6, show.legend = F) +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) +
#   scale_colour_discrete(type=c("blue"), name="") +
#   scale_y_continuous(breaks=seq(-0.5, 0.5, by = 0.25)) +
#   coord_cartesian(ylim = c(-0.5, 0.5)) +
#   #labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.98),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_HourlyGrowthRate_077",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Create GrowthCurve plot

```{r create GrowthCurve plot, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# 
# MCImportAll %>%
#   filter(Strain == "PE-rich_048") %>% 
#   # filter(time <200) %>% 
#  #filter(time >48) %>% 
#   filter(Run != 77) %>% 
#   ggplot() +
#   geom_point(aes(x = time, y = mu_Averh), colour = "brown1", alpha = 0.2, show.legend = T) +
#   geom_line(aes(x = time, y = svr_pred, colour = as.factor(Strain)), size = 0.6, show.legend = F) +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) +
#   scale_colour_discrete(type=c("blue"), name="") +
#   scale_y_continuous(breaks=seq(-0.5, 0.5, by = 0.25)) +
#   coord_cartesian(ylim = c(-0.5, 0.5)) +
#   #labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.98),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_HourlyGrowthRate_048",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

```{r create GrowthCurve plot, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# 
# MCImportAll %>%
#   filter(Strain == "PE-rich_127") %>% 
#   # filter(time <200) %>% 
#  #filter(time >48) %>% 
#   filter(Run != 77) %>% 
#   ggplot() +
#   geom_point(aes(x = time, y = mu_Averh), colour = "brown4", alpha = 0.2, show.legend = T) +
#   geom_line(aes(x = time, y = svr_pred, colour = as.factor(Strain)), size = 0.6, show.legend = F) +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) +
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) +
#   scale_colour_discrete(type=c("blue"), name="") +
#   scale_y_continuous(breaks=seq(-0.5, 0.5, by = 0.25)) +
#   coord_cartesian(ylim = c(-0.5, 0.5)) +
#   #labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.98),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_HourlyGrowthRate_127",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```


```{r}
# rm(sc, result, MCDataHourSVR, MCData)
```







# Support Vector regression for single run

```{r}
# library(e1071)
# svr_model <- svm(mu_deltaODwindow ~ time, data = MCDataHourTest, kernel = 'radial',
#                  cost = 24, gamma = 100)
# resid_svr <- MCDataHourTest$mu_deltaODwindow - predict(svr_model)
# sqrt(mean(resid_svr ^ 2))
```

```{r}
# ## test residuals
# test_resid_svr <- MCDataHourTest$mu_deltaODwindow - predict(svr_model, MCDataHourTest)
# ## test RMSE
# sqrt(mean(test_resid_svr ^ 2))
# ## R Squared
# cor(MCDataHourTest$mu_deltaODwindow, predict(svr_model, MCDataHourTest)) ^ 2
# 
# MCDataHourTest$svr_pred <- predict(svr_model, MCDataHourTest)
```

```{r}
# MCDataHourTest <-MCDataHour %>% 
#   select(c(time, Day, mu_deltaODwindow, Actinic_photonsm2h, Tube)) %>% 
#   filter(Tube == 5) %>% 
#   #filter(time >= 24) %>% 
#    # filter(time <= 240) %>% 
#   drop_na(mu_deltaODwindow)
#   
# myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(100, 1000000))
# 
# MCDataHourTest |>
#   ggplot() +
#   geom_point(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
#   geom_line(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
#   sc +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
#   facet_grid(cols = vars(Tube)) +
#   theme_bw()
```









