---
title: "Process_SolisenseLRCData"
author:
- Mireille Savoie
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_SolisenseLRCData.Rmd process PicoDiel_Imported_SolisenseLight_LRC.Rds stored in ImportedSolisenseData folder, process Turner Catalog (google sheet) and PicoDiel_Processed_PigmentsAll.Rds stored in ProcessedPigmentsData folder (contained cell/L for each ToD) and creates PicoDiel_Processed_SolisenseJVPSII.Rds stored in ProcessedSolisenseData folder.

# Load Libraries

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(googledrive)
library(googlesheets4)
library(readxl)
library(Cairo) #for greek symbols
library(data.table)
library(purrr)
library(minpack.lm) #Standard 'nls' framework that uses 'nls.lm' for fitting
```

# Read ActPARCrossCal Rds from FluorO2Calibrations project existing on GitHub

```{r read existing Rds}
#"..", "..", takes up two levels in the directory path
Path <- file.path("..", "..", "FluorO2Calibrations", "CalibrationData")

ActPARCrossCal <- read_rds(file.path(Path, "SolisenseInformation_DCCrossParam.Rds"))

ActPARCrossCal <- ActPARCrossCal %>% 
  mutate(Slope = `estimate_LIFT_Gen_Developer.cal`,
         Slope_SE = `std.error_LIFT_Gen_Developer.cal`) %>% 
  select(c(DCLamp, Models, Slope, Slope_SE))

#intercept set to 0 in lm in SolisenseInformation.Rproj/SolisenseCalibCompare.Rmd
```

# Set up conversions

```{r conversions}
us_s <- 1000000
photons_umol <- 6.022E17 #Avogardo
A2_m2 <- 1E20 #for sigma -> angstrom (Å) – a metric unit of length equal to 10^−10 m
```

# Read MetaData

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```



----------------------------------------- Old Software -----------------------------------------------


# Set Project Variables from old software (OS)

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
# Project <- "PicoDiel"
# DataOut <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData")
# 
# zip_file <- file.path("..", "Data", "RawData", "SolisenseOSData.zip")
# 
# SolisenseFilesOS <- unzip(zip_file, list = TRUE)
# SolisenseFilesOS <- SolisenseFilesOS[grepl(".csv$", SolisenseFilesOS$Name), "Name"]
# print(SolisenseFilesOS)
# 
# FileID <- "fit"
# FileEncode <- "UTF-8"
# Delimiter <- ","
# HeaderRows <- 0
```

# Set up delim_plus function

```{r set up read_delim_plus, warning = FALSE, echo=FALSE}
# read_delim_plus <- function(flnm, delimiter, headerrows, fileencode) {
#   fread(flnm, skip = headerrows, sep = delimiter, header = TRUE, encoding = fileencode) %>%
#     mutate(Filename = flnm)
# }
# 
# SolFitsOS <- SolisenseFilesOS %>%
#   map_df(~read_delim_plus(flnm = unzip(zip_file, exdir = tempdir())[which(unzip(zip_file, list = TRUE)$Name == .)], delimiter = Delimiter, headerrows = HeaderRows, fileencode = FileEncode))
```

# Import and prepare files

```{r tidy SolFitsTrim}
# SolFitsTrimOS <- SolFitsOS %>%
#   filter(!grepl("----", DATE)) %>% 
#   select(-c("RFID_User_Data", "Barcode_Data", "PIF",  "Lon", "Lat", "GPS_stat", "LEDSel", "S/N_raw", "PAR_3", "PAR_4", "PAR_5", "PAR_6", "TPQ_PSI", "QBP_Size", "Alp4QA", "Tau4QA", "Alp1PQ", "Tau1PQ", "Alp2PQ", "Tau2PQ", "Alp3PQ", "Tau3PQ", "ETR", "V58")) %>% # remove superfluous columns for unfit data
# 
#   mutate(Filename = str_remove(string = Filename, pattern = "/RawData/SolisenseOS.zip/"),
#          Filename = str_remove(string = Filename, pattern = "_fit.csv")
#          ) %>%
#   separate(Filename, into = c("fp1", "fp2", "fp3", "fp4", "fp5", "fp6", "fp7", "Project", "RunDateTime", "SampleID", "Ex_WL"), sep = "([\\/\\_])", remove = FALSE) %>%
#   mutate(RunDateTime = ymd_hm(RunDateTime),
#          TIME = as.character(TIME)) %>%  #time-column may be read in as factor, and as.character changes it to numeric; using lubdridate::hms would only change the format to 13H 4M 2S but does not work later to merge into one DateTime-column
#   mutate(SourceDataFile = `Source DataFile`,
#          ObsDate = DATE,
#          ObsTime = TIME) %>%
#   mutate(Ex_WL = as.factor(as.numeric(Ex_WL))) %>%
#   mutate(across(.cols = c(Light_1:fQB), .fns = as.numeric)) %>%
#   mutate(StartDateTimeSol = RunDateTime) %>%
#   mutate(nm445 = Light_1,
#          nm470 = Light_2,
#          nm505 = Light_3,
#          nm535 = Light_4,
#          nm590 = Light_5,
#          IR = Light_6) %>%
#   drop_na(StartDateTimeSol) %>%
#   mutate(ObsTime = hms(ObsTime),
#          ObsDate = ymd(ObsDate)) %>%
#   mutate(ObsDateTime = ymd_hms(paste(ObsDate, ObsTime))) %>%
#   relocate(ObsDateTime, .after = ObsTime) %>%
#   relocate(SampleID, .before = ObsDate) %>%
#   #mutate(FvFm=as.numeric(FvFm)) %>%
#   select(-c(Light_1,Light_2,Light_3,Light_4,Light_5,Light_6,`Source DataFile`,DATE,TIME,RunDateTime, fp1, fp2, fp3, fp4, fp5, fp6, fp7, Project))
# 
# #for consistency add TempCont column
# SolFitsTrimOS <- SolFitsTrimOS %>%
#   mutate(TempCont = "TC") %>%
#   mutate(FvFm = Fv/Fm*1) %>%
#   select(-c("Fv/Fm"))
```


----------------------------------------- New Software -----------------------------------------------

# Set Project Variables from new software (NS)

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
# Project <- "PicoDiel"
# DataOut <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData")
# 
# zip_file <- file.path("..", "Data", "RawData", "SolisenseNSData.zip")
# 
# SolisenseFilesNS <- unzip(zip_file, list = TRUE)
# SolisenseFilesNS <- SolisenseFilesNS[grepl(".csv$", SolisenseFilesNS$Name), "Name"]
# print(SolisenseFilesNS)
# 
# FileID <- "fit"
# FileEncode <- "UTF-8"
# Delimiter <- ","
# HeaderRows <- 0
```

# Set up read_delim_plus function

```{r set up read_delim_plus, warning = FALSE, echo=FALSE}
# read_delim_plus <- function(flnm, delimiter, headerrows, fileencode) {
#   fread(flnm, skip = headerrows, sep = delimiter, header = TRUE, encoding = fileencode) %>%
#     mutate(Filename = flnm)
# }
# 
# SolFitsNS <- SolisenseFilesNS %>%
#   map_df(~read_delim_plus(flnm = unzip(zip_file, exdir = tempdir())[which(unzip(zip_file, list = TRUE)$Name == .)], delimiter = Delimiter, headerrows = HeaderRows, fileencode = FileEncode))
```

# Import and prepare files
Issue with read_delim_plus reading in files in .zip; filename different on PC and MacOS

```{r tidy SolFitsTrim}
# SolFitsTrimNS <- SolFitsNS %>%
#   filter(!grepl("----", DATE)) %>% 
#   select(-c("RFID_User_Data", "Barcode_Data", "PIF",  "Lon", "Lat", "GPS_stat", "LEDSel")) %>% # remove superfluous columns for unfit data
#   mutate(Filename = str_remove(string = Filename, pattern = "/RawData/SolisenseNSData.zip/"),
#          Filename = str_remove(string = Filename, pattern = "_fit.csv")
#          ) %>%
#   separate(Filename, into = c("fp1", "fp2", "fp3", "fp4", "fp5", "fp6", "fp7", "Project", "RunDateTime", "SampleID", "Ex_WL"), sep = "([\\/\\_])", remove = FALSE) %>%
#   mutate(RunDateTime = ymd_hm(RunDateTime),
#          TIME = as.character(TIME)) %>%  #time-column may be read in as factor, and as.character changes it to numeric; using lubdridate::hms would only change the format to 13H 4M 2S but does not work later to merge into one DateTime-column
#   mutate(SourceDataFile = `Source DataFile`,
#          ObsDate = DATE,
#          ObsTime = TIME) %>%
#   mutate(Ex_WL = as.factor(as.numeric(Ex_WL))) %>%
#   mutate(across(.cols = c(Light_1:Fv), .fns = as.numeric)) %>%
#   mutate(StartDateTimeSol = RunDateTime) %>%
#   mutate(nm445 = Light_1,
#          nm470 = Light_2,
#          nm505 = Light_3,
#          nm535 = Light_4,
#          nm590 = Light_5,
#          IR = Light_6) %>%
# drop_na(StartDateTimeSol) %>% 
#   mutate(ObsTime = hms(ObsTime),
#          ObsDate = ymd(ObsDate)) %>%
#   mutate(ObsDateTime = ymd_hms(paste(ObsDate, ObsTime))) %>%
#   relocate(ObsDateTime, .after = ObsTime) %>%
#   relocate(SampleID, .before = ObsDate) %>%
#   #mutate(FvFm=as.numeric(FvFm)) %>%
#   select(-c(Light_1,Light_2,Light_3,Light_4,Light_5,Light_6,`Source DataFile`,DATE,TIME,RunDateTime, fp1, fp2, fp3, fp4, fp5, fp6, fp7, Project))
# 
# #for consistency add TempCont column
# SolFitsTrimNS <- SolFitsTrimNS %>%
#   mutate(TempCont = "TC") %>%
#   mutate(FvFm = Fv/Fm*1) %>%
#   select(-c("Fv/Fm"))
```


# Choose the same variables to merge df taken from old and new Solisense software

```{r}
# SolFitsTrimOS<-SolFitsTrimOS %>% 
#   select(c(SampleID, Time__mSec, Fo, Fm, Fv, FvFm, Tau1QA, Tau2QA, Tau3QA, Alp1QA, Alp2QA, Alp3QA, Alpha, Ek, Pmax, SourceDataFile, Filename, ObsDate, ObsTime, ObsDateTime, Ex_WL, StartDateTimeSol, nm445, nm470, nm505, nm535, nm590, IR, TempCont, Sig))
# 
# SolFitsTrimNS<-SolFitsTrimNS %>% 
#   select(c(SampleID, Time__mSec, Fo, Fm, Fv, FvFm, Tau1QA, Tau2QA, Tau3QA, Alp1QA, Alp2QA, Alp3QA, Alpha, Ek, Pmax, SourceDataFile, Filename, ObsDate, ObsTime, ObsDateTime, Ex_WL, StartDateTimeSol, nm445, nm470, nm505, nm535, nm590, IR, TempCont, Sig))
```

# Merge df from old and new Software 

```{r combine data from old and new Software}
# SolFitsOSNS <-rbind(SolFitsTrimOS, SolFitsTrimNS)
```

# Add ActPARcorr with proper correction factors for TC and no TC

```{r Add ActPARcorr}
# #Intercepts for cross conversions set to 0.
# SolFitsOSNS <- SolFitsOSNS %>% 
#   mutate(nm445Corr = case_when(TempCont == "TC" ~ nm445 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr1_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
#                                  TempCont == "noTC" ~ nm445 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr1_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
#          nm470Corr = case_when(TempCont == "TC" ~ nm470 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr2_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
#                                  TempCont == "noTC" ~ nm470 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr2_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
#          nm505Corr = case_when(TempCont == "TC" ~ nm505 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr3_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
#                                  TempCont == "noTC" ~ nm505 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr3_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
#            nm535Corr = case_when(TempCont == "TC" ~ nm535 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr4_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
#                                  TempCont == "noTC" ~ nm535 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr4_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
#           nm590Corr = case_when(TempCont == "TC" ~ nm590 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr5_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
#                                  TempCont == "noTC" ~ nm590 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr5_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
#           IRCorr = case_when(TempCont == "TC" ~ IR * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "PwrIR_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
#                                  TempCont == "noTC" ~ IR * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "PwrIR_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]))
# 
# SolFitsOSNS <- SolFitsOSNS %>%
#   mutate(ActPAR = nm445 + nm470 + nm505 + nm535 + nm590 + IR) %>%  
#   mutate(ActPARCorr = nm445Corr + nm470Corr + nm505Corr + nm535Corr + nm590Corr + IRCorr)
```

# Preparing df for further analysis

```{r durations}
# #generate column with duration of light step in s
# #add a column adding Dark1s based upon any step < 5 s
# #replace NA for first dark with nominal 181;  issue will be changing durations of light steps across each run
# SolFitsOSNS <- SolFitsOSNS %>%
#   group_by(SourceDataFile, Filename, SampleID, ObsDate, Ex_WL, TempCont) %>%
#   mutate(Step_s = replace_na(as.numeric(ObsDateTime - lag(ObsDateTime)), 181), .after = ObsDateTime) %>% 
#   mutate(LR_s = as.numeric(ObsDateTime - ObsDateTime[1]), .after = Step_s) %>%
#   mutate(Dark1s = if_else(Step_s > 5, 0, 1), .after = Step_s) %>%
#   relocate(Ex_WL, .after = Dark1s) %>%
#   relocate(ActPAR, .after = Ex_WL) %>%
#   ungroup()
```

# Merge Solisense data with MetaData

```{r combine Solisense and MetaData catalog, warning = FALSE, echo=FALSE}
# SolFitsMeta <- CultureCatalog %>%
#   left_join(., SolFitsOSNS, by = c("SampleID" = "SampleID")) 
```

# Estimate parameters using Oxborough & Baker 1997 for Fo'

```{r estimate parameters, warning = FALSE, echo=FALSE}

# SolFitsMeta <- SolFitsMeta %>%
#   group_by(SourceDataFile, Filename, SampleID, ObsDate, Ex_WL, TempCont) %>%
#   mutate(Sig_m2psii = Sig/A2_m2,
#          Fodark = Fo[1],
#          Fmdark = Fm[1],
#          Sigdark = Sig[1],
#          Sigdark_m2psii = Sigdark/A2_m2,
#          ActPARCorr_photonsm2s = ActPARCorr *  photons_umol, 
#          TauAv = ((Tau1QA * Alp1QA) + (Tau2QA * Alp2QA))/(Alp1QA + Alp2QA), 
#          Ctauav = 1/(1 + (Sig_m2psii * ActPARCorr_photonsm2s * (TauAv/us_s))), 
#          aLHIIdark = (Fmdark * Fodark)/(Fmdark - Fodark),
#          Fomin = min(Fo, na.rm = TRUE),
#          Fmmax = max(Fm, na.rm = TRUE),
#          Sigmax = max(Sig, na.rm = TRUE),
#          Sigmax_m2psii = Sigmax/A2_m2,
#          FoOxbo = Fomin/(((Fmmax - Fomin)/Fmmax) + (Fomin/Fm)),
#          qpOxbo = (Fm - Fo)/(Fm - FoOxbo),
#          aLHIIOxbomax = (Fmmax * FoOxbo)/(Fmmax - FoOxbo),
#          JVPSII_aLHIIOxbomax = ActPARCorr_photonsm2s * aLHIIOxbomax * FvFm,
#          ETRCtauav = Sig_m2psii * Ctauav * ActPARCorr_photonsm2s,
#          ETRqpOxbo = Sig_m2psii * qpOxbo * ActPARCorr_photonsm2s,
#          JVPSII_ETRtauav_FoSig = ETRCtauav * Fomin/Sigmax_m2psii, #Sigmax converted A2_m2
#          JVPSII_ETRqpOxbo_FoSig = ETRqpOxbo * Fomin/Sigmax_m2psii,
#          JVPSII_ETRtauav_aLHII_Sig = ETRCtauav * aLHIIOxbomax/Sigmax_m2psii,
#          JVPSII_ETRqpOxbo_aLHII_Sig = ETRqpOxbo * aLHIIOxbomax/Sigmax_m2psii) %>%
#   ungroup()
```

# Convert Sig_m2psii to Sig_nm2psii and Sigdark_m2psii to Sigdark_nm2psii and calculated number of days when measurements were made

```{r convert Sigma}
# SolFitsMeta <- SolFitsMeta %>%
# mutate(Sig_nm2psii=Sig_m2psii*1000000000000000000) %>% 
# mutate(Sigdark_nm2psii=Sigdark_m2psii*1000000000000000000)   
```

```{r calculate E_days and Time_h}
# SolFitsMeta<- SolFitsMeta %>%
# group_by(SampleID) %>%
#   arrange(ObsDate) %>%
#   mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
# ungroup()
# 
# SolFitsMeta<- SolFitsMeta %>%
#   mutate(Time_h = E_days*24)
```

```{r}
# SolFitsMeta<- SolFitsMeta %>%
#   drop_na(Sig)
```

# Remove outliers

```{r}
# SolFitsMeta445<- SolFitsMeta %>%
#   filter(Ex_WL == 445) %>% 
#   filter(Sig<250)
#   
# SolFitsMeta590<- SolFitsMeta %>% 
#   filter(Ex_WL == 590)
# 
# SolFitsMeta<-rbind(SolFitsMeta445, SolFitsMeta590)
# 
# rm(SolFitsMeta445, SolFitsMeta590)
```

# Save rds for further analysis

```{r save rds}
# saveRDS(SolFitsMeta, file.path(DataOut, paste(Project, "Imported_SolisenseLight_LRC.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


------------------------------------------------------------------------------------------------------------------------- 

# Set Project Variables 

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
Project <- "PicoDiel"
DataIn <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData")
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
# FileID <- "fit"
# FileEncode <- "UTF-8"
# Delimiter <- ","
# HeaderRows <- 0
```

# Read Imported Solisense

```{r read locally stored metadata from rds}
SolFitsMetaRaw <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedSolisenseData", "PicoDiel_Imported_SolisenseLight_LRC.Rds"))

SolFitsMetaRaw<-SolFitsMetaRaw
```

# Create preliminary plots 

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsMetaRaw %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = Sig, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  facet_grid(rows = vars(Ex_WL), cols = vars(Photoperiod)) +
  theme_bw()

```
# Change variable names for consistency

```{r}
SolFitsMetaRaw <- SolFitsMetaRaw %>%
  rename(FilenameSolisense=Filename)
```

# Create smaller value to for Platt model

```{r}
SolFitsMeta<-SolFitsMetaRaw %>%
  mutate(JVPSII_aLHIIOxbomax = JVPSII_aLHIIOxbomax/1e22) %>%
  mutate(JVPSII_ETRtauav_FoSig = JVPSII_ETRtauav_FoSig/1e22) %>%
  mutate(JVPSII_ETRqpOxbo_FoSig = JVPSII_ETRqpOxbo_FoSig/1e22) %>%
  mutate(JVPSII_ETRtauav_aLHII_Sig = JVPSII_ETRtauav_aLHII_Sig/1e22) %>%
  mutate(JVPSII_ETRqpOxbo_aLHII_Sig = JVPSII_ETRqpOxbo_aLHII_Sig/1e22)
```


# Create preliminary plots 

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsMeta %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_ETRqpOxbo_FoSig, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  facet_grid(cols = vars(Ex_WL, Photoperiod), rows = vars(Par_ue)) +
  theme_bw()

```


# Fit LRC for JVPSII to allow selection of specific JVPSII for different growth light levels.

```{r}
grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

#`%notin%` <- negate(`%in%`)
# "ObsDate", "ObsTime","ObsDateTime","E_days", "Time_h", "StartDateTimeSol", "Time_mSec"
# filter(SampleID %notin% c("SySl1266") | ObsDate %notin% c("2022-06-14") | Ex_WL %notin% c(445)) %>%

SolFitsMetaLRC <- SolFitsMeta %>%
  nest(data = -c("SampleID", "Run", "Strain" ,"ExpDate","Par_ue", "Photoperiod", "O2", "WL", "MC", "Tube","Ex_WL","LightShape", "ExpEndDate", "PARPhotonDose_day", "ObsDate", "E_days")) %>% #head(50) %>% 
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(JVPSII_ETRqpOxbo_FoSig ~ grcplatt(I = ActPARCorr, a, b, Pmax),
         data = .x,
         control = list(maxiter = 100),
         start = list(a = 0.1/30, b = 0.01/800, Pmax = 6),lower = c(0, 0, 0))))) %>%
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance)))


# GRCplatt_PredictSolFits <- SolFitsMetaLRC %>%
#   unnest(GRCplatt_Predict)%>%
#   unnest(GRCplatt_Param)
#   
```

# Create preliminary plot - Example

```{r prelim plot}
SolFitsMetaLRC |> 
  unnest(GRCplatt_Predict) |>
  filter(Strain == "BA48R") %>% 
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 16) |>
ggplot() +
  geom_point(aes(ActPARCorr, JVPSII_ETRqpOxbo_FoSig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.8, size = 3.5, show.legend = T) +
  geom_line(aes(ActPARCorr, .fitted), colour = "black", linetype = "dotted") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain, Par_ue, Photoperiod, E_days), labeller = label_parsed) +
  theme_bw()

```

Use Peak Par_ue and 1/2 Peak Par_ue to estimate growth JVPSII for each combination
-use 'Pluck' to reach into GRCplatt_Predict to get a, b, Pmax; or
-unnest, pivot wider to get a, b, Pmax

```{r growth light JVPSII}

SolFitsMetaLRCGrowth <- SolFitsMetaLRC |>
  unnest(GRCplatt_Param) |>
  select(-c(statistic, p.value, GRCplatt_Predict, GRCplatt_Glance)) |> #remove (temporarily) to make pivot_wider easier
  pivot_wider(names_from = term, values_from = c(estimate, std.error)) |>
  mutate(JVPSII_Par_ue = grcplatt(I = Par_ue, a = estimate_a, estimate_b, estimate_Pmax),
         JVPSII_HalfPar_ue = grcplatt(I = (0.5*Par_ue), a = estimate_a, estimate_b, estimate_Pmax))

 
head(SolFitsMetaLRCGrowth) 
```

# Test plots of Growth Par_ue and 1/2 Growth Par_ue estimates for JVPSII
```{r growth JVPSII}
SolFitsMetaLRCGrowth |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()

SolFitsMetaLRCGrowth |>
  filter(Strain == "BA48R") |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()

SolFitsMetaLRCGrowth |>
  filter(Strain == "BA77G") |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()
```
# Variable names used in Data Dictionary

```{r}
colnames(SolFitsMeta)
```


# Save Rds for further analysis

```{r save rds}
# saveRDS(SolFitsMetaLRCGrowth, file.path(DataOut, paste(Project, "Imported_Solisense_LRC.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```



------------------------------------------------------# Add Turner Catalog--------------------------------------------------

# Load Turner catalog

```{r load turner catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
Turnercatalog<- read_sheet("https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0")

as.data.frame(Turnercatalog)
ChlData <- Turnercatalog 

ChlData <- ChlData %>%  
  mutate(TurChl_ugL = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept)) %>% 
  mutate(DATE = ymd(`DATE`)) %>% 
  rename(SampleID=CultureID) %>% 
  rename(ObsDate=DATE) %>% 
  select(c(SampleID, ObsDate, TurChl_ugL)) %>% 
  filter(TurChl_ugL<212354.754)  #outliers

```

# Calculate Chl mean from 3 technical replica

```{r}
ChlData <- ChlData %>%
  group_by(SampleID, ObsDate) %>%
  summarize(SampleID, ObsDate, TurChl_ugL,
            meanTurChl_ugL = mean(TurChl_ugL),
            sdTurChl_ugL = sd(TurChl_ugL)) %>%
  ungroup()
```


# Merge JVPSII with chlorophyll Turner data 
It is "bigger" df b/c I have 3 replica for Turner

```{r}
SolFitsExpStTurner <- ChlData %>%
  full_join(., SolFitsMetaLRCGrowth, by = c("SampleID"="SampleID", "ObsDate"="ObsDate")) %>% 
  drop_na(Strain)
```
```{r}
SolFitsExpStTurner<-SolFitsExpStTurner %>%  
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 
```

# Filter only revelant strains

```{r}
SolFitsExpStTurner<-SolFitsExpStTurner %>%  
  filter(Strain=="PC-rich_056" | Strain == "PC-rich_077" | Strain == "PE-rich_048" | Strain == "PE-rich_127")
```


# Create preliminary JVPSII vs Chl Turner (ug/L) plot

```{r preliminary plots, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = TurChl_ugL, y = JVPSII_Par_ue, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_Par_ue, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_HalfPar_ue, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()


SolFitsExpStTurner %>% 
  filter(Ex_WL == 445) %>% 
  filter(Photoperiod == 24) %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_Par_ue, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Photoperiod, Par_ue), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()
```

--------------------------------- Adding cell_L ------------------------------

```{r set project variables}
Project <- "PicoDiel"
DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedPigmentsData", fsep = .Platform$file.sep)
```

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read pigments File}
#df ontained mean OD per day from Multiculti and Abs from Olis spectra for selected nm. Based on this I calculated pigments per mL and per cell (pg/cell)

MCPigmentAllFile <- "../Data/ProcessedData/ProcessedPigmentsData/PicoDiel_Processed_PigmentsAll.Rds"
MCPigmentAllFileName <- str_split(string = MCPigmentAllFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
MCPigmentAll <- readRDS(MCPigmentAllFile)  %>%
  ungroup()
```

```{r}
# colnames(MCPigmentAll)

MCPigmentAll<-MCPigmentAll %>% 
  select(-c(Phase, ChlaugmL, CarugmL, PEugmL, PCugmL, APCugmL, PhycougmL, CarChlaRatio, PhycoChlaRatio, PEPCRatio, Chlapgcell, Carpgcell, PEpgcell, PCpgcell, APCpgcell, Phycopgcell, meanOD720_h, meanDeltaOD_h, AchivePreStationary, dayRound_tmaxAG, MaxAG, MaxDG, MC))

```

```{r}
# MCPigmentAll <- MCPigmentAll %>%
#   filter(ToD==12) # When I choose 12 (peak) then I loose a few data point from 12h and 900UE
```

```{r}
SolFitsAll <- MCPigmentAll %>%
  full_join(., SolFitsExpStTurner, by = c("SampleID"="SampleID", "Strain"="Strain", "Run"="Run", "Tube"="Tube", "Par_ue" = "Par_ue", "Photoperiod"="Photoperiod", "O2"="O2", "WL"="WL", "LightShape"="LightShape", "ExpDate"="ExpDate", "ExpEndDate"="ExpEndDate", "PARPhotonDose_day"="PARPhotonDose_day","E_days"="E_days"))
```

```{r}
SolFitsAll<-SolFitsAll %>% 
  drop_na(JVPSII_Par_ue)
```

# Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAll %>%
  filter(Ex_WL == 445) %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsAll %>%
  filter(Ex_WL == 445) %>% 
  ggplot() +
  geom_point(aes(x = TurChl_ugL, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsAll %>%
  filter(Ex_WL == 445) %>% 
  ggplot() +
  geom_point(aes(x = cellL_OD680, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
```


# Choose only exp data

```{r choose only exp data}
O1 <- SolFitsAll %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 600 | Par_ue == 900) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days <= 4)

O2 <- SolFitsAll %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 16) 
  #filter(E_days < 9)

O3 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 16) %>%
  filter(E_days <= 4)

O4 <- SolFitsAll %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 16) 
  #filter(E_days <= 14)

O5 <- SolFitsAll %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 8 | Photoperiod == 12) 
  #filter(E_days <=14)

O6 <- SolFitsAll %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 8) 
  #filter(E_days <=14)

O7 <- SolFitsAll %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 12) %>%
  filter(E_days <=10)

O8 <- SolFitsAll %>%
  filter(Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 8 | Photoperiod == 12) 
  #filter(E_days <=10)

O9 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 8 | Photoperiod == 12) %>%
  filter(E_days <=7)

O10 <- SolFitsAll %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days <= 8)

SolFitsAllExp <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)
```

# Choose only Stationary data 

```{r choose only St data}
O1 <- SolFitsAll %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 600 | Par_ue == 900) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days > 4)

O2 <- SolFitsAll %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >14)

O3 <- SolFitsAll %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O4 <- SolFitsAll %>%
  filter(Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 8 | Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O5 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 16) %>%
  filter(E_days >=6)

O6 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 12) %>%
  filter(E_days >=4)

O6 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 8) %>%
  filter(E_days >7)

SolFitsAllSt <-rbind(O1, O2, O3, O4, O5, O6)

rm(O1, O2, O3, O4, O5, O6)
```

# Combine Exp and St data

```{r}
  SolFitsAllExp$Phase <- 'Exponential'
  SolFitsAllSt$Phase <- 'Pre-stationary'

  SolFitsAllExpSt <-rbind(SolFitsAllExp, SolFitsAllSt)
```


# Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllExpSt %>%
  filter(Ex_WL == 445) %>% 
  filter(Phase == "Exponential") %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Phase, Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsAllExpSt %>%
  filter(Ex_WL == 445) %>% 
  filter(Phase == "Exponential") %>% 
  #filter(Photoperiod == 8) %>% 
  ggplot() +
  geom_point(aes(x = TurChl_ugL, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Phase, Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsAllExpSt %>%
  filter(Ex_WL == 445) %>% 
  filter(Phase == "Exponential") %>% 
  ggplot() +
  geom_point(aes(x = cellL_OD680, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Phase, Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
```
# Save rds for further analysis

```{r save rds}
saveRDS(SolFitsAllExpSt, file.path(DataOut, paste(Project, "Processed_SolisenseJVPSII.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(SolFitsAllExpSt)
```





Oxborough & Baker 1997 for Fo'

Oxborough, K., & Baker, N. R. (1997). Resolving chlorophyll a fluorescence images of photosynthetic efficiency into photochemical and non-photochemical components–calculation of qP and Fv-/Fm-; without measuring Fo. Photosynthesis research, 54, 135-142.

Oxborough, K., & Baker, N. R. (1997). An instrument capable of imaging chlorophyll a fluorescence from intact leaves at very low irradiance and at cellular and subcellular levels of organization. Plant, Cell & Environment, 20(12), 1473-1483.

Oxborough, K., Moore, C. M., Suggett, D. J., Lawson, T., Chan, H. G., & Geider, R. J. (2012). Direct estimation of functional PSII reaction center concentration and PSII electron flux on a volume basis: a new approach to the analysis of Fast Repetition Rate fluorometry (FRRf) data. Limnology and Oceanography: Methods, 10(3), 142-154.

Suggett, D. J., Moore, C. M., Oxborough, K., & Geider, R. J. (2006). Fast repetition rate (FRR) chlorophyll a fluorescence induction measurements. West Molesey: Chelsea Technologies Group, 1-53.




Berge, J., Grant, S., Bjørgum, R., Cohen, J. H., McKee, D., Johnsen, G., Zolich, A., Kopec, T. P., Vogedes, D. L., UiT The Arctic University of Norway (2021).Time series (2017) of irradiance in the PAR (photosynthetically active radiation) region measured under the dome of a light observatory in the Arctic  (Ny-Ålesund, Svalbard, Norway) derived from an USSIMO spectroradiometer [Data set]. Norstore. https://doi.org/10.11582/2021.00040

https://archive.norstore.no/pages/public/datasetDetail.jsf?id=10.11582/2021.00040

PAR is approximated as an integral of micromolespersec=(uirr/(h*c/(lambda*1e-9)))/microavo for wavelengths(lambda) in range from 400 to 700nm, where: uirr = USSIMO irradiance for wavelength equal to lambda, h=6.63e-34 [Js], c=3.00e+08 [m/s], microavo=6.022e17.





Fast Repetition Rate fluorometry (FRRf, Kolber et al. 1998) 

σPSII - Effective absorption cross section of PSII photochemistry in darkness -> A2 (quanta)-1 or m2
ρ - Connectivity between PSII reaction centres in darkness

σPSII′ - Effective absorption cross section of PSII photochemistry under actinic light -> A2 (quanta)-1 or m2
ρ′ - Connectivity between PSII reaction centres under actinic light

TauPSII - Minimum turnover time of PSII photochemistry -> s-1

F0 or F0’ (Minimum fluorescence in darkness or Minimum fluorescence under actinic light)
Fm or Fm’ (Maximum fluorescence in darkness or Maximum fluorescence under actinic light)
F’ (or Fs; Steady state fluorescence at any point)
Fv = Fm-F0 (Variable fluorescence in darkness)
Fv’ = Fm’-F0’ (Variable fluorescence under actinic light)
Fq′ = (Fm′ - F′) (Difference between Fm′ and F′)

Fv/Fm = (Fm-F0)/Fm (The maximum PSII quantum yield/Maximum photochemical efficiency)
Fv’/Fm’ = (Fm’- F0’)/Fm’ (Maximum PSII efficiency under actinic light)

ΦPSII = (Fm’- F’)/Fm’ = Fq′/Fm′ (Photochemical efficiency under actinic light)

qP = (Fm’- F’)/(Fm’-F0’) = (Fm′ - F′)/Fv′ = Fq′/Fv′ (PSII efficiency factor under actinic light; photochemical quenching coefficient) 

NPQ =(Fm-Fm’)/Fm’ (Non-photochemical quenching coefficien)


ETR = PPFD * aPSII * PSII photochemical efficiency (ΦPSII)

ETR^RCII = PPFD * σPSII * Fq′/Fm′ (or ΦPSII) * 21.683

ETR^chl = PPFD * σPSII * n PSII * Fq′/Fm′ (or ΦPSII) * 21.683


FRR fluorescence provides a direct measure of light absorption per unit PSII reaction centres (σPSII).

ETR, called the relative electron transport rate, is the product of the effective photochemical yield of
PSII (ΦPSII) and photosynthetic photon flux density

ETR^RCII(chl) - RCII (Chlorophyll a)-normalised rate of electron transfer by PSII -> mol e- g chla-1 h-1

ETR^chl is the chlorophylla-specific rate of electron transfer (mol e- mol chla-1 h-1 ).

PPFD (=E) - Photosynthetically active photon flux density -> μmol m-2 s-1

a^chlPSII - a^chl only used for PSII photochemistry -> m2 mg chla-1

(factor 21.683 converts seconds to hours, μmol e- to mol e- and A2 quanta-1 to m2 mol RCII-1)

nPSII - photosynthetic unit size of PSII

JVPSII - PSII flux per unit volume -> electrons m–3 s–1

[RCII] - concentration of functional PS II reaction centers -> m-3

aLHII - LHII (light harvesting complex II) absorption coefficient -> m-1


