---
title: "Process_GrowthSymmetryData"
author:
- Mireille Savoie
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_GrowthSymmetryData.Rmd processes Growth Symmetry (GS) catalog from a google sheet. This .Rmd generates PicoDiel_Processed_GrowthSymmetryData.Rds (stored in Data/ProcessedData/ProcessedGrowthSymmetryData folder) and plots (stored in Output/Figures folder).

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)
library(stringi)
```

```{r set project variables}
Project <- "PicoDiel"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthSymmetryData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileID <- "Smooth"
FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# Read MetaData

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```

# Read Growth Symmetry (GS) catalog

```{r load local GS catalog, results = "hide", message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
# this is the URL or ID of a Sheet readable by anyone (with a link)
GScatalog<- read_sheet("https://docs.google.com/spreadsheets/d/1zqH6iYlqMPigyloLKJPeVWugmcnmgJ-eMU3gLkR6FSU/edit#gid=0")

as.data.frame(GScatalog)
GScatalog <- GScatalog 
```

# Preparing df for further analysis

```{r prepare data - mutate as numeric, calculate AccLen, DecLen, GS (growth symmetry)}
GScatalog <- GScatalog %>% 
  mutate(Acc_perc = as.numeric(Acc_perc)) %>% 
  mutate(Dec_perc = as.numeric(Dec_perc)) %>% 
  mutate(AccDecRatio_perc = Acc_perc/Dec_perc) %>% 
  mutate(Par_ue = as.numeric(Par_ue)) %>% 
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(tMaxAG = as.numeric(tMaxAG)) %>%
  mutate(tMaxDG = as.numeric(tMaxDG)) %>%
  mutate(PhotoperiodTstart_h=as.numeric(PhotoperiodTstart_h)) %>% 
  mutate(PhotoperiodTend_h=as.numeric(PhotoperiodTend_h)) %>% 
  mutate(AccLen = tMaxDG-PhotoperiodTstart_h) %>% 
  mutate(DecLen = PhotoperiodTend_h-tMaxDG) %>% 
  mutate(GS = AccLen/DecLen) %>% 
  mutate(TDG = as.numeric(TDG)) 
```

# Merge GS catalog with MetaData

```{r merge GS catalog with MetaData, warning = FALSE, echo=FALSE}
GScatalogMeta <- CultureCatalog %>%
  left_join(., GScatalog, by = c("Strain" = "Strain", "Photoperiod"="Photoperiod", "Par_ue"="Par_ue","WL"="WL", "O2"="O2")) 
```

# Filtering unrelated values and outliers

```{r cleaning unrelated values and outliers}
GScatalogMeta<-GScatalogMeta %>% 
  filter(Photoperiod!=24) %>% 
  filter(AccDecRatio_perc<10)
  
GScatalogMeta1 <-GScatalogMeta %>% 
  filter(PARPhotonDose_day>=19440000) %>% 
  filter(GS<=2)
GScatalogMeta2 <-GScatalogMeta %>% 
  filter(PARPhotonDose_day<19440000) %>% 
filter(GS<4)

GScatalogMeta<-rbind(GScatalogMeta1,GScatalogMeta2)
rm(GScatalogMeta1,GScatalogMeta2)
```

# Calculate mean of GS from every day (every peak in exp and pre-stationary phase)

```{r calculate mean of GS, warning = FALSE}
GScatalogMeta<-GScatalogMeta %>% 
  group_by(Strain, Photoperiod, Par_ue, Phase) %>%
  summarize(Run, SampleID, Strain, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, MC, Tube, O2, LightShape, ExpEndDate, PhotoperiodTstart_h, PhotoperiodTend_h,tMaxDG,tMaxAG, Phase, AchivePreStationary, MaxDG, MaxAG, Acc_perc, Dec_perc, Strain, Par_ue, Photoperiod, O2, WL, OD680start, OD680end, TDG, AccDecRatio_perc, AccLen, DecLen, GS, 
            meanAccLen = mean(AccLen), 
            sdAccLen = sd(AccLen),
            meanDecLen = mean(DecLen), 
            sdDecLen = sd(DecLen),
            meanGS = mean(GS), 
            sdGS = sd(GS)) %>%  
  ungroup() 
```
# Rename strain names, create facets labels, and create horizontal lines for plot

```{r rename strain names for plot}
GScatalogMeta<-GScatalogMeta %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))
```

```{r create facets labels for plot}
GScatalogMeta$facetsPar_ue = factor(GScatalogMeta$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
GScatalogMeta$facetsPhotoperiod = factor(GScatalogMeta$WL, labels = c("Photoperiod~(h)"))
GScatalogMeta$facetsStrain = factor(GScatalogMeta$O2, labels = c("Strain"))
GScatalogMeta$facetsPhase = factor(GScatalogMeta$WL, labels = c("Phase~of~growth"))
```

```{r create df to show hline}
data_hlineGS8 <- data.frame(Photoperiod= c(8),facets2= c("Photoperiod~(h)"),value = c(4))
data_hlineGS12 <- data.frame(Photoperiod= c(12),facets2= c("Photoperiod~(h)"),value = c(6))
data_hlineGS16 <- data.frame(Photoperiod= c(16),facets2= c("Photoperiod~(h)"),value = c(8))
```

# Filter 3 data points from stationary phase

```{r}
GScatalogMeta_1<-GScatalogMeta %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Strain != "PE-rich_127")
GScatalogMeta_2<-GScatalogMeta %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Strain == "PE-rich_127") %>%
  filter(Par_ue ==300) %>%
  filter(GS < 0.65)
GScatalogMeta_3<-GScatalogMeta %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Strain == "PE-rich_127") %>%
  filter(Par_ue ==90| Par_ue ==180 | Par_ue ==900)
GScatalogMeta_4<-GScatalogMeta %>%
  filter(Phase == "Exponential")
GScatalogMetaFit<-rbind(GScatalogMeta_1, GScatalogMeta_2, GScatalogMeta_3, GScatalogMeta_4)
  rm(GScatalogMeta_1, GScatalogMeta_2, GScatalogMeta_3, GScatalogMeta_4)
```

# Fit the data to exponential decays

```{r fitting exponential decays, warning = FALSE}
GScatalogMetaExpSt <-GScatalogMetaFit %>% 
  drop_na(GS) %>%
  #filter(Phase == "Exponential") %>% 
  select(c(GS, PARPhotonDose_day, Strain, Phase, O2, WL)) 

# Fit the data
fitted <- GScatalogMetaExpSt %>% 
  nest(-c(Strain, Phase, O2, WL)) %>%
  mutate(
    fit = map(data, ~nls(GS ~ SSasymp(PARPhotonDose_day, yf, y0, log_alpha), data = .)),
    tidied = map(fit, tidy),
    augmented = map(fit, augment)) 

# Produce a table of fit parameters: y0, yf, alpha
fitted_GS_Param<-fitted %>% 
  unnest(tidied) %>% 
  select(Strain, Phase, term, estimate) %>% 
pivot_wider(., names_from = c(term), values_from = c(estimate)) %>% 
  mutate(alpha = exp(log_alpha)) 

augmented<-fitted  %>%
  unnest(augmented) %>%
  select(c(Strain, Phase, O2, WL, PARPhotonDose_day,GS, .fitted)) 

```

# Create GS and AccLen plots

```{r create GS plot, fig.height = 8, fig.width = 8, warning = FALSE}

data_text_y0Exp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('y0 = 2.6', 'y0 = 1.6', 'y0 = 1.2', 'y0 = 1.4'))
data_text_yfExp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('yf = 0.8', 'yf = 0.5', 'yf = 0.3', 'yf = 0.5'))
data_text_lambdaExp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('\u03BB = 3.4e-07', '\u03BB = 1.7e-07', '\u03BB = 1.2e-07', '\u03BB = 2.1e-07'))

data_text_y0St<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('y0 = NA', '  y0 = 3.8', 'y0 = 0.6', 'y0 = 0.6'))
data_text_yfSt<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('yf = 0.7', 'yf = 0.4', 'yf = 0.3', 'yf = 0.2'))
data_text_lambdaSt<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('\u03BB = NA', '     \u03BB = 1.8e-06', '     \u03BB = 7.8e-08', '     \u03BB = 6.3e-08'))

# data_text_AnovaExp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, b', ' ANOVA, \u03B1 = 0.05, ab'))

data_text_AnovaExp56<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PC-rich_056"),  label = c('a'))
data_text_AnovaExp77<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PC-rich_077"),  label = c("a"))
data_text_AnovaExp48<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PE-rich_048"),  label = c("b"))
data_text_AnovaExp127<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PE-rich_127"),  label = c("ab"))

data_text_AnovaSt56<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_056"),  label = c('a'))
data_text_AnovaSt77<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_077"),  label = c("ab"))
data_text_AnovaSt48<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_048"),  label = c("ab"))
data_text_AnovaSt127<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_127"),  label = c("b"))

data_text_AnovaExp56P<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PC-rich_056"),  label = c('A'))
data_text_AnovaExp77P<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PC-rich_077"),  label = c("A"))
data_text_AnovaExp48P<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PE-rich_048"),  label = c("A"))
data_text_AnovaExp127P<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PE-rich_127"),  label = c("A"))

data_text_AnovaSt56P<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_056"),  label = c('B'))
data_text_AnovaSt77P<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_077"),  label = c("B"))
data_text_AnovaSt48P<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_048"),  label = c("B"))
data_text_AnovaSt127P<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_127"),  label = c("B"))

data_text_AnovaPhase<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05'))

WL.labs <- c("Phase of growth")
names(WL.labs) <- c("WW")
O2.labs <- c("Strain")
names(O2.labs) <- c(21)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

  ggplot(GScatalogMetaFit, aes(x = PARPhotonDose_day, y = meanGS)) +
  geom_point(aes(x = PARPhotonDose_day, y = meanGS, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T, GScatalogMetaFit) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = meanGS - sdGS, ymax = meanGS + sdGS, colour = as.factor(Par_ue)), show.legend = F, width=0, size=0.3, GScatalogMetaFit) +
  geom_point(aes(x = PARPhotonDose_day, y = GS, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, alpha = 0.8, show.legend = F, GScatalogMetaFit) +
    
  geom_line(aes(PARPhotonDose_day, .fitted), colour = "blue", size = 0.3, linetype = "solid", show.legend = F, augmented) +
  geom_hline(yintercept = 1, linetype="dashed", size=0.4, colour = "cornsilk4") +

  geom_text(data=data_text_y0Exp, aes(x=23000000, y=3, label=label), size=3.5) +
  geom_text(data=data_text_yfExp, aes(x=23000000, y=2.5, label=label), size=3.5) +
  geom_text(data=data_text_lambdaExp, aes(x=24000000, y=2.0, label=label), size=3.5) +
  
  geom_text(data=data_text_y0St, aes(x=2400000, y=3, label=label), size=3.5) +
  geom_text(data=data_text_yfSt, aes(x=2400000, y=2.5, label=label), size=3.5) +
  geom_text(data=data_text_lambdaSt, aes(x=2400000, y=2.0, label=label), size=3.5) +
    
  # geom_text(data=data_text_AnovaExp, aes(x=5000000, y=0, label=label), colour = "blue", size=3.5) +
  # geom_text(data=data_text_AnovaSt, aes(x=5000000, y=0, label=label), colour = "blue", size=3.5) +
    
  geom_text(data=data_text_AnovaExp56, aes(x=25000000, y=1.3, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp77, aes(x=25000000, y=1.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp48, aes(x=25000000, y=0.9, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp127, aes(x=25000000, y=1.0, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaSt56, aes(x=8000000, y=1.1, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt77, aes(x=8000000, y=1.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt48, aes(x=25000000, y=0.8, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt127, aes(x=25000000, y=0.7, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaExp56P, aes(x=25000000, y=0.6, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp77P, aes(x=25000000, y=0.2, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp48P, aes(x=25000000, y=0.1, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp127P, aes(x=25000000, y=0.2, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaSt56P, aes(x=8000000, y=0.4, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt77P, aes(x=8000000, y=0.1, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt48P, aes(x=25000000, y=0.1, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt127P, aes(x=25000000, y=0.0, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaPhase, aes(x=7000000, y=-0.2, label=label), colour = "blue", size=4) +
    
  scale_shape_manual(values = c(15, 16, 17), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "khaki2"), name="", labels = lab2) +
  #scale_x_continuous(label=scientific_10) +
  scale_x_continuous(breaks=seq(0, 27000000, by = 10000000), label=scientific_10) +
  coord_cartesian(xlim = c(0, 27000000), ylim = c(-0.5, 3.5)) +
    
  guides(color = guide_legend(order = 1), shape  = guide_legend(order = 0)) +
  labs(y = "Diel growth symmetry (AccLen/DecLen ratio)", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(WL, Phase), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.90,0.90),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=11))
```


# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_GS",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Cleaning the environment

```{r}
rm(data_text_y0Exp, data_text_yfExp, data_text_lambdaExp, data_text_y0St, data_text_yfSt, data_text_lambdaSt, data_text_AnovaExp56P, data_text_AnovaExp77P, data_text_AnovaExp48P, data_text_AnovaExp127P, data_text_AnovaExp56, data_text_AnovaExp77, data_text_AnovaExp48, data_text_AnovaExp127, data_text_AnovaSt56P, data_text_AnovaSt77P, data_text_AnovaSt48P, data_text_AnovaSt127P, data_text_AnovaSt56, data_text_AnovaSt77, data_text_AnovaSt48, data_text_AnovaSt127)
```

# Calculated Anova and Tukey test from data points

```{r calculated statistics}
GScatalogMetaFitStats<-GScatalogMetaFit 
  #filter(Par_ue != 600) 

GScatalogMetaFitStats$Par_ue <- factor(GScatalogMetaFitStats$Par_ue)
GScatalogMetaFitStats$Photoperiod <- factor(GScatalogMetaFitStats$Photoperiod)
GScatalogMetaFitStats$Strain <- factor(GScatalogMetaFitStats$Strain)
GScatalogMetaFitStats$Phase <- factor(GScatalogMetaFitStats$Phase)
GScatalogMetaFitStats$PARPhotonDose_day <- factor(GScatalogMetaFitStats$PARPhotonDose_day)

# Three way Anova with interactions
model<-aov(GS~PARPhotonDose_day*Phase*Strain, data=GScatalogMetaFitStats)
Anova_GS<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
#TukeyHSDTest_GS<-TukeyHSD(model, which = c("PARPhotonDose_day", "Phase", "Strain"))
```

# Save Rds that create stats and tables

```{r}
saveRDS(Anova_GS, file.path(TableRdsPath, paste(Project, "Anova_GS.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Calculated Anova and Tukey test from exponential decay parameters

```{r calculated statistics}

fitted_GS_Param[2, 4] = NA
fitted_GS_Param[2, 6] = NA

GS_Param<-fitted_GS_Param 
  
GSStats<-GS_Param 
GSStats2<-rbind(GSStats, GSStats)
GSStats2$Strain <- factor(GSStats2$Strain)
GSStats2$Phase <- factor(GSStats2$Phase)

# Two-way Anova
model<-aov(y0~Strain*Phase, data=GSStats2)
AnovaTest_GS_y0<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_GS_y0$Parameter <- 'y0'

model<-aov(yf~Strain*Phase, data=GSStats2)
AnovaTest_GS_yf<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_GS_yf$Parameter <- 'yf'

model<-aov(alpha~Strain*Phase, data=GSStats2)
AnovaTest_GS_alpha<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_GS_alpha$Parameter <- 'alpha'

Anova_GS_Param<-rbind(AnovaTest_GS_y0, AnovaTest_GS_yf, AnovaTest_GS_alpha)

rm(AnovaTest_GS_y0, AnovaTest_GS_yf, AnovaTest_GS_alpha, GSStats, GSStats2, model, fitted_GS_Param)
```

# Save Rds that create stats and tables

```{r}
# saveRDS(AnovaTest_GS_Param, file.path(TableRdsPath, paste(Project, "Anova_GS_Param.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Exstracting models for each fit

```{r}
fittedmodel<-fitted  %>%
  select(c(Strain, Phase, fit))
```

# Anova from the model - compare fits

```{r}
#1->048 St
#2->056 St
#3->077 St
#4->127 St
#5->127 Exp
#6->048 Exp
#7->056 Exp
#8->077 Exp

#Comparing model for strains from Exp phase
fittedmodelStrainExp<-fittedmodel 
  anova056077Exp<-anova(fittedmodelStrainExp[[3]][[7]], fittedmodelStrainExp[[3]][[8]])
  anova056077Exp$FitComparison <- '056_077_Exp'
  anova048127Exp<-anova(fittedmodelStrainExp[[3]][[6]], fittedmodelStrainExp[[3]][[5]])
  anova048127Exp$FitComparison <- '048_127_Exp'
  anova056048Exp<-anova(fittedmodelStrainExp[[3]][[7]], fittedmodelStrainExp[[3]][[6]])
  anova056048Exp$FitComparison <- '056_048_Exp'
  anova077048Exp<-anova(fittedmodelStrainExp[[3]][[8]], fittedmodelStrainExp[[3]][[6]])
  anova077048Exp$FitComparison <- '077_048_Exp'
  anova056127Exp<-anova(fittedmodelStrainExp[[3]][[7]], fittedmodelStrainExp[[3]][[5]])
  anova056127Exp$FitComparison <- '056_127_Exp'
  anova077127Exp<-anova(fittedmodelStrainExp[[3]][[8]], fittedmodelStrainExp[[3]][[5]])
  anova077127Exp$FitComparison <- '077_127_Exp'
  anovaStrainExp<-rbind(anova056077Exp, anova048127Exp, anova056048Exp, anova077048Exp, anova056127Exp, anova077127Exp)
  anovaStrainExp <-anovaStrainExp %>% 
  drop_na(Df) 
  rm(anova056077Exp, anova048127Exp, anova056048Exp, anova077048Exp, anova056127Exp, anova077127Exp)

#Comparing model for strains from St phase
fittedmodelStrainSt<-fittedmodel 
  anova056077St<-anova(fittedmodelStrainSt[[3]][[2]], fittedmodelStrainSt[[3]][[3]])
  anova056077St$FitComparison <- '056_077_St'
  anova048127St<-anova(fittedmodelStrainSt[[3]][[1]], fittedmodelStrainSt[[3]][[4]])
  anova048127St$FitComparison <- '048_127_St'
  anova056048St<-anova(fittedmodelStrainSt[[3]][[1]], fittedmodelStrainSt[[3]][[2]])
  anova056048St$FitComparison <- '056_048_St'
  anova077048St<-anova(fittedmodelStrainSt[[3]][[3]], fittedmodelStrainSt[[3]][[1]])
  anova077048St$FitComparison <- '077_048_St'
  anova056127St<-anova(fittedmodelStrainSt[[3]][[2]], fittedmodelStrainSt[[3]][[4]])
  anova056127St$FitComparison <- '056_127_St'
  anova077127St<-anova(fittedmodelStrainSt[[3]][[3]], fittedmodelStrainSt[[3]][[4]])
  anova077127St$FitComparison <- '077_127_St'
  anovaStrainSt<-rbind(anova056077St, anova048127St, anova056048St, anova077048St, anova056127St, anova077127St)
  anovaStrainSt <-anovaStrainSt %>% 
  drop_na(Df) 
  rm(anova056077St, anova048127St, anova056048St, anova077048St, anova056127St, anova077127St)
  
#Comparing model for each strains from different phase (Exp vs St)
fittedmodelPhase<-fittedmodel 
  anova056ExpSt<-anova(fittedmodelPhase[[3]][[7]], fittedmodelPhase[[3]][[2]])
  anova056ExpSt$FitComparison <- '056_Exp_St'
  anova077ExpSt<-anova(fittedmodelPhase[[3]][[8]], fittedmodelPhase[[3]][[3]])
  anova077ExpSt$FitComparison <- '077_Exp_St'
  anova048ExpSt<-anova(fittedmodelPhase[[3]][[6]], fittedmodelPhase[[3]][[1]])
  anova048ExpSt$FitComparison <- '048_Exp_St'
  anova127ExpSt<-anova(fittedmodelPhase[[3]][[5]], fittedmodelPhase[[3]][[4]])
  anova127ExpSt$FitComparison <- '127_Exp_St'
  anovaPhase<-rbind(anova056ExpSt, anova077ExpSt, anova048ExpSt, anova127ExpSt)
  anovaPhase <-anovaPhase %>% 
  drop_na(Df) 
  rm(anova056ExpSt, anova077ExpSt, anova048ExpSt, anova127ExpSt)

  Anova_GS_Model<-rbind(anovaStrainExp, anovaStrainSt, anovaPhase)
  
  rm(anovaStrainExp, anovaStrainSt, anovaPhase)
```

# Save Rds that create stats and tables

```{r}
saveRDS(Anova_GS_Model, file.path(TableRdsPath, paste(Project, "Anova_GS_Model.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


```{r AccLen Plot, warning = FALSE}
data_text_8<- data.frame(facetsPhase = c("Phase~of~growth", "Phase~of~growth"), Phase = c("Exponential"), facetsStrain=c("Strain", "Strain", "Strain", "Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('Max light at   8h', 'Max light at   8h', 'Max light at   8h', 'Max light at   8h'))

data_text_12<- data.frame(facetsPhase = c("Phase~of~growth", "Phase~of~growth"), Phase = c("Exponential"), facetsStrain=c("Strain", "Strain", "Strain", "Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('Max light at 12h', 'Max light at 12h', 'Max light at 12h', 'Max light at 12h'))

data_text_16<- data.frame(facetsPhase = c("Phase~of~growth", "Phase~of~growth"), Phase = c("Exponential"), facetsStrain=c("Strain", "Strain", "Strain", "Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('Max light at 16h', 'Max light at 16h', 'Max light at 16h', 'Max light at 16h'))


scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

GScatalogMeta %>%
  filter(meanAccLen>0) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = meanAccLen, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T) +
  # geom_line(aes(x = PARPhotonDose_day, y = meanAccLen, colour = as.factor(Par_ue)), size = 0.3, show.legend = F) +
  geom_line(aes(x = PARPhotonDose_day, y = meanAccLen, linetype=as.factor(Photoperiod)), colour = "blue", size=0.3, show.legend = F) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = meanAccLen - sdAccLen, ymax = meanAccLen + sdAccLen, colour = as.factor(Par_ue)), show.legend = F, width=0, size=0.3) +
  geom_point(aes(x = PARPhotonDose_day, y = AccLen, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, alpha = 0.8, show.legend = F) +
  geom_text(data=data_text_8, aes(x=32000000, y=3.5, label=label), size=2.8) +
  geom_text(data=data_text_12, aes(x=32000000, y=5.5, label=label), size=2.8) +
  geom_text(data=data_text_16, aes(x=32000000, y=7.5, label=label), size=2.8) +
  geom_hline(data = data_hlineGS8, aes(yintercept = value), linetype="dashed", size=0.4, colour = "cornsilk4") +
  geom_hline(data = data_hlineGS12, aes(yintercept = value), linetype="dashed", size=0.4, colour = "cornsilk4") +
  geom_hline(data = data_hlineGS16, aes(yintercept = value), linetype="dashed", size=0.4, colour = "cornsilk4") +
  scale_shape_manual(values = c(15, 16, 17), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "khaki2"), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "solid", "solid"), name="", labels = lab1) +
  scale_x_continuous(breaks=seq(0, 30000000, by = 10000000), label=scientific_10) +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(ylim = c(0, 12), xlim = c(0, 36000000)) +
  guides(color = guide_legend(order = 1), shape  = guide_legend(order = 0)) +
  labs(y = "Hours of photoperiod to reach maximum hourly growth", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.90,0.9),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
# ggsave(file = file.path(PlotsPath, paste("AccLen2_Plot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

```{r AccLen Plot, fig.height = 8, fig.width = 8, warning = FALSE}
data_text_8<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain=c("Strain", "Strain", "Strain", "Strain"), Strain  = c("PC-rich_077"),  label = c('Time to max light for  8h photoperiod'))

data_text_12<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain=c("Strain", "Strain", "Strain", "Strain"), Strain  = c("PC-rich_077"),  label = c('Time to max light for 12h photoperiod'))

data_text_16<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain=c("Strain", "Strain", "Strain", "Strain"), Strain  = c("PC-rich_077"),  label = c("Time to max light for 16h photoperiod"))


scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

GScatalogMeta %>%
  filter(meanAccLen>0) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = meanAccLen, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T) +
  geom_line(aes(x = PARPhotonDose_day, y = meanAccLen, colour = as.factor(Par_ue)), size = 0.3, show.legend = F) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = meanAccLen - sdAccLen, ymax = meanAccLen + sdAccLen, colour = as.factor(Par_ue)), show.legend = F, width=0, size=0.3) +
  geom_point(aes(x = PARPhotonDose_day, y = AccLen, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, alpha = 0.8, show.legend = F) +
  geom_text(data=data_text_8, aes(x=24000000, y=3.5, label=label), size=2.8) +
  geom_text(data=data_text_12, aes(x=24000000, y=5.5, label=label), size=2.8) +
  geom_text(data=data_text_16, aes(x=24000000, y=7.5, label=label), size=2.8) +
  geom_hline(data = data_hlineGS8, aes(yintercept = value), linetype="dashed", size=0.4, colour = "cornsilk4") +
  geom_hline(data = data_hlineGS12, aes(yintercept = value), linetype="dashed", size=0.4, colour = "cornsilk4") +
  geom_hline(data = data_hlineGS16, aes(yintercept = value), linetype="dashed", size=0.4, colour = "cornsilk4") +
  scale_shape_manual(values = c(15, 16, 17), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "khaki2"), name="", labels = lab2) +
  scale_x_continuous(breaks=seq(0, 30000000, by = 10000000), label=scientific_10) +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(ylim = c(0, 12), xlim = c(0, 37000000)) +
  
  guides(color = guide_legend(order = 1), shape  = guide_legend(order = 0)) +
  labs(y = "Hours of photoperiod to reach maximum hourly growth", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.9,0.9),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_AccLen",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

```{r AccLen Plot, fig.height = 8, fig.width = 8, warning = FALSE}

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

GScatalogMeta %>%
  filter(meanAccLen>0) %>% 
  ggplot() +
  geom_point(aes(x = Photoperiod, y = AccLen, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, alpha = 0.8, show.legend = F) +
  geom_errorbar(aes(x = Photoperiod, ymin = meanAccLen - sdAccLen, ymax = meanAccLen + sdAccLen, colour = as.factor(Par_ue)), show.legend = F, width=0) +
  geom_point(aes(x = Photoperiod, y = meanAccLen, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "khaki2"), name="", labels = lab2) +
  geom_abline(slope = 0.5, intercept = 0, linetype = "dashed", size=0.4, colour = "cornsilk4") +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(ylim = c(0, 14)) +
  guides(color = guide_legend(order = 1), shape  = guide_legend(order = 0)) +
  labs(y = "Hours of photoperiod to reach maximum hourly growth", x = "Photoperiod (h)") +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        panel.spacing.x = unit(1,"lines"),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.6,0.91),
        #legend.margin = margin(0,-0.5,0,0, unit="cm"),
        legend.key.height= unit(0.0005, 'cm'),
        legend.spacing.y = unit(-0.2, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_AccLen",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```


# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG values

```{r}
tMaxAGLines_056<-GScatalogMeta %>% 
  filter(Strain == "PC-rich_056") %>% 
  select(c(Par_ue, Photoperiod, facetsPar_ue, facetsPhotoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_077<-GScatalogMeta %>% 
  filter(Strain == "PC-rich_077") %>% 
  select(c(Par_ue, Photoperiod, facetsPar_ue, facetsPhotoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_048<-GScatalogMeta %>% 
  filter(Strain == "PE-rich_048") %>% 
  select(c(Par_ue, Photoperiod, facetsPar_ue, facetsPhotoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_127<-GScatalogMeta %>% 
  filter(Strain == "PE-rich_127") %>% 
  select(c(Par_ue, Photoperiod, facetsPar_ue, facetsPhotoperiod, tMaxAG)) %>% 
  unique()
```

# Create TDG plot

```{r Create TDG plot, warning = FALSE}
GScatalogMeta %>%
  filter(Photoperiod != 24) %>% 
  ggplot() +
  geom_point(aes(x = PhotoperiodTend_h, y = TDG, colour = as.factor(Strain)), size = 3, alpha = 0.8, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4", size=0.4) +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3", size=0.4) +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4", size=0.4) +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1", size=0.4) +
labs(y = "TDG ("~OD[680]~")", x = "Elapsed time (h)") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_x_continuous(breaks=seq(0, 300, by = 100)) +
  coord_cartesian(xlim = c(0, 350)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        legend.background = element_rect(fill="transparent"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #panel.spacing.x=unit(0.9, "lines"),
        legend.position = c(0.1,0.93),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.title = element_blank(),
        legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_TDG",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Removed unnecessary files from the environment

```{r cleaning the environment}
rm(data_hlineGS8, data_hlineGS12, data_hlineGS16, GScatalog, GScatalogMetaExp,  CultureCatalog, tMaxAGLines_056, tMaxAGLines_077, tMaxAGLines_048, tMaxAGLines_127, GScatalogMetaFinalPlot, GSMetaExp, GSMetaExpPlot, data_text_8, data_text_12, data_text_16, augmented, data_text_AnovaPhase, fitted, fittedmodel, fittedmodelPhase, fittedmodelStrainExp, fittedmodelStrainSt, GScatalogMetaExpSt, GScatalogMetaFit, GScatalogMetaFitStats)
```

# Save Rds that create plot

```{r}
# saveRDS(GScatalogMeta, file.path(FigRdsPath, paste(Project, "Fig_GrowthSymmetry_1.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
# 
# saveRDS(augmented, file.path(FigRdsPath, paste(Project, "Fig_GrowthSymmetry_2.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


# Save Rds for further analysis

```{r save Rds}
saveRDS(GScatalogMeta, file.path(DataOut, paste(Project, "Processed_GrowthSymmetryData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(GScatalogMeta)
```



# Performed a t-test using the coefficients from a non-linear model in R.
Welch Two Sample t-test - Welch's t-test

In statistics, Welch's t-test, or unequal variances t-test, is a two-sample location test which is used to test the (null) hypothesis that two populations have equal means. It is more reliable when the two samples have unequal variances and possibly unequal sample sizes. These tests are often referred to as "unpaired" or "independent samples" t-tests, as they are typically applied when the statistical units underlying the two samples being compared are non-overlapping. Given that Welch's t-test has been less popular than Student's t-test and may be less familiar to readers, a more informative name is "Welch's unequal variances t-test" — or "unequal variances t-test" for brevity.
```{r}
# #1->048 St
# #2->056 St
# #3->077 St
# #4->127 St
# #5->127 Exp
# #6->048 Exp
# #7->056 Exp
# #8->077 Exp
# fittedmodelStrainExp<-fittedmodel 
# 
# model1 <- fittedmodelStrainExp[[3]][[1]]
# model2 <- fittedmodelStrainExp[[3]][[2]]
# model3 <- fittedmodelStrainExp[[3]][[3]]
# model4 <- fittedmodelStrainExp[[3]][[4]]
# model5 <- fittedmodelStrainExp[[3]][[5]]
# model6 <- fittedmodelStrainExp[[3]][[6]]
# model7 <- fittedmodelStrainExp[[3]][[7]]
# model8 <- fittedmodelStrainExp[[3]][[8]]
# # Extract coefficients
# coef_model1 <- coef(model1)
# coef_model2 <- coef(model2)
# coef_model3 <- coef(model3)
# coef_model4 <- coef(model4)
# coef_model5 <- coef(model5)
# coef_model6 <- coef(model6)
# coef_model7 <- coef(model7)
# coef_model8 <- coef(model8)
# # Perform t-test
# t_test_result_056_077_Exp <- t.test(coef_model7, coef_model8) #'056_077_Exp'
# t_test_result_048_127_Exp <- t.test(coef_model6, coef_model5) #'048_127_Exp'
# t_test_result_056_048_Exp <- t.test(coef_model7, coef_model6) #'056_048_Exp'
# t_test_result_077_048_Exp <- t.test(coef_model8, coef_model6) #'077_048_Exp'
# t_test_result_056_127_Exp <- t.test(coef_model7, coef_model5) #'056_127_Exp'
# t_test_result_077_127_Exp <- t.test(coef_model8, coef_model5) #'077_127_Exp'
# 
# # Extract relevant information
# t_test_result_056_077_Exp <- data.frame(t_test = t_test_result_056_077_Exp$statistic, p_value = t_test_result_056_077_Exp$p.value, Df = t_test_result_056_077_Exp$parameter, conf_interval_lower = t_test_result_056_077_Exp$conf.int[1], conf_interval_upper = t_test_result_056_077_Exp$conf.int[2], method = t_test_result_056_077_Exp$method, alternative = t_test_result_056_077_Exp$alternative, Fit_model = c("056_077_Exp", "056_077_Exp"))
# 
# t_test_result_048_127_Exp <- data.frame(t_test = t_test_result_048_127_Exp$statistic, p_value = t_test_result_048_127_Exp$p.value, Df = t_test_result_048_127_Exp$parameter, conf_interval_lower = t_test_result_048_127_Exp$conf.int[1], conf_interval_upper = t_test_result_048_127_Exp$conf.int[2], method = t_test_result_048_127_Exp$method, alternative = t_test_result_048_127_Exp$alternative, Fit_model = c("048_127_Exp", "048_127_Exp"))
# 
# t_test_result_056_048_Exp <- data.frame(t_test = t_test_result_056_048_Exp$statistic, p_value = t_test_result_056_048_Exp$p.value, Df = t_test_result_056_048_Exp$parameter, conf_interval_lower = t_test_result_056_048_Exp$conf.int[1], conf_interval_upper = t_test_result_056_048_Exp$conf.int[2], method = t_test_result_056_048_Exp$method, alternative = t_test_result_056_048_Exp$alternative, Fit_model = c("056_048_Exp", "056_048_Exp"))
# 
# t_test_result_077_048_Exp <- data.frame(t_test = t_test_result_077_048_Exp$statistic, p_value = t_test_result_077_048_Exp$p.value, Df = t_test_result_077_048_Exp$parameter, conf_interval_lower = t_test_result_077_048_Exp$conf.int[1], conf_interval_upper = t_test_result_077_048_Exp$conf.int[2], method = t_test_result_077_048_Exp$method, alternative = t_test_result_077_048_Exp$alternative, Fit_model = c("077_048_Exp", "077_048_Exp"))
# 
# t_test_result_056_127_Exp <- data.frame(t_test = t_test_result_056_127_Exp$statistic, p_value = t_test_result_056_127_Exp$p.value, Df = t_test_result_056_127_Exp$parameter, conf_interval_lower = t_test_result_056_127_Exp$conf.int[1], conf_interval_upper = t_test_result_056_127_Exp$conf.int[2], method = t_test_result_056_127_Exp$method, alternative = t_test_result_056_127_Exp$alternative, Fit_model = c("056_127_Exp", "056_127_Exp"))
# 
# t_test_result_077_127_Exp <- data.frame(t_test = t_test_result_077_127_Exp$statistic, p_value = t_test_result_077_127_Exp$p.value, Df = t_test_result_077_127_Exp$parameter, conf_interval_lower = t_test_result_077_127_Exp$conf.int[1], conf_interval_upper = t_test_result_077_127_Exp$conf.int[2], method = t_test_result_077_127_Exp$method, alternative = t_test_result_077_127_Exp$alternative, Fit_model = c("077_127_Exp", "077_127_Exp"))
#   
# anovaStrainExp<-rbind(t_test_result_056_077_Exp, t_test_result_048_127_Exp, t_test_result_056_048_Exp, t_test_result_077_048_Exp, t_test_result_056_127_Exp, t_test_result_077_127_Exp)
# anovaStrainExp<-anovaStrainExp %>% 
#   unique()

```

